---
output:
  pdf_document: default
  html_document: default
---
# Load necessary packages
```{r, results = 'hide', message = FALSE, warning = FALSE}
library(tidyverse)
library(taRifx)
library(ggrepel)
library(psych)
library(lavaan)
library(semPlot)
library(MVN)
library(infotheo)
source('Calculate-MutInfo.R', local = TRUE)
```

# Create dataframes for analyses
```{r}
full.df <- read.csv('C:/Users/Cole/Documents/DATA/PLIC_DATA/Collective_Surveys/Complete/Complete_Concat_CourseInfo.csv') %>%
  filter(Survey_x == 'C' | Survey_y == 'C') %>% # remove events with no CR surveys
  # remove pre-pandemic data
  mutate(V4_x = as.Date(V4_x),
         V4_y = as.Date(V4_y)) %>%
  filter(V4_y < as.Date('2020-01-01') | (is.na(V4_y) & 
                                           V4_x < as.Date('2020-01-01')))

# Remove FR scores
full.df[(full.df$Survey_x == 'F') | is.na(full.df$Q3c_x), 'PreScores'] <- NA_real_
full.df[(full.df$Survey_y == 'F') | is.na(full.df$Q3c_y), 'PostScores'] <- NA_real_
full.df <- full.df %>%
  filter(!is.na(PreScores) | !is.na(PostScores))

nrow(full.df)

# identify columns corresponding to scores on a question and columns corresponding to 
# 'other' response choices...we don't care about the 'other' response choices since this 
# method evaluates utility of response choices and we have to keep the 'other' response 
# choices regardless
ScoresVec <- c('Q1Bs', 'Q1Ds', 'Q1Es', 'Q2Bs', 'Q2Ds', 'Q2Es', 'Q3Bs', 'Q3Ds', 
               'Q3Es', 'Q4Bs')
OthersVec <- c('Q1b_19', 'Q1d_10', 'Q1e_12', 'Q2b_38', 'Q2d_11', 'Q2e_11', 
               'Q3b_10', 'Q3d_29', 'Q3e_8', 'Q4b_11')

GetPrePostSurveys <- function(df, survey) {
  # retrieves response choices and scores on either the pre or post survey only
  if(survey == 'PRE') {
    # all presurvey columns have '_x' appended, postsurveys have '_y'
    appendix <- 'x'
    df.survey <- df %>%
      # filter only closed response surveys where a presurvey total score 
      # exists...the Q3c filter is used to identify most recent versions of the '
      # survey where Q3c was included
      filter(!is.na(PreScores)) 
  } else {
    appendix <- 'y'
    df.survey <- df %>%
      filter(!is.na(PostScores))
  }
  
  df.survey <- df.survey %>%
    select(c(grep(paste('((Q1b|Q1d|Q1e|Q2b|Q2d|Q2e|Q3b|Q3d|Q3e|Q4b)_[0-9]*)', 
                        appendix, sep = '_'),
                  names(.))), paste(ScoresVec, appendix, sep = '_')) %>%
    `colnames<-`(gsub(x = names(.), pattern = paste("\\", appendix, sep = '_'), 
                      replacement = "")) %>%
    select(-OthersVec)
}

df_Pre <- GetPrePostSurveys(full.df, 'PRE')
df_Post <- GetPrePostSurveys(full.df, 'POST')

df <- rbind(df_Pre, df_Post)
print(nrow(df))

char_vars <- lapply(df, class) == "character"
df[, char_vars] <- lapply(df[, char_vars], as.factor)

df <- df %>%
  japply(., which(sapply(., class) == 'factor'), function(x) as.numeric(levels(x))[x])

df[is.na(df)] <- 0
df_Questions <- df[, ScoresVec]
df_Items <- df[, !names(df) %in% ScoresVec]
```

# CFA on dataset with hypothesized model
```{r}
PLIC.model.HYP <- ' models  =~ Q1Bs + Q2Bs + Q3Bs + Q3Ds
              methods =~ Q1Ds + Q2Ds + Q4Bs
              actions =~ Q1Es + Q2Es + Q3Es '

mod.cfa.HYP <- cfa(PLIC.model.HYP, data = df_Questions, std.lv = TRUE, 
                   estimator = 'ML')

summary(mod.cfa.HYP, fit.measures = TRUE, modindices = FALSE, standardized = TRUE)
resid(mod.cfa.HYP)
cor(df_Questions)

semPaths(mod.cfa.HYP, what = 'diagram', whatLabels = 'stand', layout = 'tree2', 
         residuals = FALSE, nCharNodes = 10, edge.color = 'black', 
         edge.label.cex = 2, 
         curve = 2, label.scale = FALSE, nodeLabels = c('Q1B', 'Q2B', 'Q3B', 'Q3D',
                                                        'Q1D', 'Q2D', 'Q4B', 'Q1E',
                                                        'Q2E', 'Q3E', 
                                                        'Evaluate\nModels', 
                                                        'Evaluate\nMethods', 
                                                        'Suggest\nFollow-ups'), 
         rotation = 2, sizeMan = 8, sizeLat = 18, width = 4, height = 5, 
         filetype = 'png', filename = 'Figures/CFA', mar = c(1, 6, 1, 2))
```

# Calculate and discretize factor scores
```{r}
scores.df <- data.frame(lavPredict(mod.cfa.HYP))

# calculate optimal number of bins to discretize each of the factor scores
N_models <- floor((max(scores.df$models) - min(scores.df$models))/
                    (3.5 * sd(scores.df$models)/(nrow(scores.df)^(1/3))))
N_methods <- floor((max(scores.df$methods) - min(scores.df$methods))/
                     (3.5 * sd(scores.df$methods)/(nrow(scores.df)^(1/3))))
N_actions <- floor((max(scores.df$actions) - min(scores.df$actions))/
                     (3.5 * sd(scores.df$actions)/(nrow(scores.df)^(1/3))))

N_models
N_methods
N_actions

scores <- data.frame(discretize(scores.df$models, nbins = N_models),
                     discretize(scores.df$methods, nbins = N_methods), 
                     discretize(scores.df$actions, nbins = N_actions))
colnames(scores) <- c('models', 'methods', 'actions')
```

# Mutual information between item response choices and individual factors

## Mutual information for item response choices with models factor
```{r}
Models.df <- df_Items[, grep('Q1b|Q2b|Q3b|Q3d', names(df_Items))]

Models.MI.df <- MI.CI(Models.df, scores$models, reps = 100)

# we highlight these specific response choices for reasons discussed in text
labels.list <- c('Q2B_9', 'Q2B_21', 'Q3B_9', 'Q3B_21', 'Q2B_11', 'Q3B_11', 
                 'Q2B_8', 'Q3B_23')

png('Figures/MutInfo_Models.png')
ggplot(Models.MI.df, aes(x = Prop.Sel, y = MI, color = Question, 
                         shape = Question)) +
  geom_point(size = 3.5, alpha = 0.25) +
  geom_errorbar(aes(ymin = CI.Low, ymax = CI.High), width = 0.01, size = 1, 
                alpha = 0.25) +
  geom_point(data = Models.MI.df[Models.MI.df[, 'Item'] %in% labels.list,], 
             aes(x = Prop.Sel, y = MI, color = Question), size = 3.5) +
  geom_errorbar(data = Models.MI.df[Models.MI.df[, 'Item'] %in% labels.list,], 
                aes(ymin = CI.Low, ymax = CI.High), width = 0.01, size = 0.8, 
                alpha = 1) +
  scale_shape_manual(values = c(15, 16, 17, 18)) +
  scale_color_manual(values = c("#0072b2", "#d55e00", "#009e73", "#009e73")) +
  scale_fill_manual(values = labels.list) +
  geom_label_repel(data = subset(Models.MI.df, Item %in% labels.list),
                  aes(x = Prop.Sel, y = MI, color = Question, label = Item), 
                  nudge_x = 0.05, nudge_y = 0.03, size = 6, show.legend = FALSE) +
  theme_classic() +
  theme(text = element_text(size = 18)) +
  labs(x = 'Fraction of times selected', y = 'Mutual information (bits)') +
  ylim(0, 0.31)
dev.off()
```

## Mutual information for item response choices with methods factor
```{r}
Methods.df <- df_Items[, grep('Q1d|Q2d|Q4b', names(df_Items))]

Methods.MI.df <- MI.CI(Methods.df, scores$methods, reps = 100)

labels.list <- c('Q1D_61', 'Q1D_63', 'Q2D_35', 'Q2D_4', 'Q1D_3', 'Q2D_33', 'Q4B_4')

png('Figures/MutInfo_Methods.png')
ggplot(Methods.MI.df, aes(x = Prop.Sel, y = MI, color = Question, 
                          shape = Question)) +
  geom_point(size = 3.5, alpha = 0.25) +
  geom_errorbar(aes(ymin = CI.Low, ymax = CI.High), width = 0.01, size = 1, 
                alpha = 0.25) +
  geom_point(data = Methods.MI.df[Methods.MI.df[, 'Item'] %in% labels.list,], 
             aes(x = Prop.Sel, y = MI, color = Question), size = 3.5) +
  geom_errorbar(data = Methods.MI.df[Methods.MI.df[, 'Item'] %in% labels.list,], 
                aes(ymin = CI.Low, ymax = CI.High), width = 0.01, size = 0.8, 
                alpha = 1) +
  scale_shape_manual(values = c(15, 16, 17)) +
  scale_color_manual(values = c("#0072b2", "#d55e00", "#cc79a7")) +
  scale_fill_manual(values = labels.list) +
  geom_label_repel(data = subset(Methods.MI.df, Item %in% labels.list),
            aes(x = Prop.Sel, y = MI, color = Question, label = Item), 
            nudge_x = 0.02, nudge_y = 0.06, size = 6, show.legend = FALSE) +
  theme_classic() +
  theme(text = element_text(size = 18)) +
  labs(x = 'Fraction of times selected', y = 'Mutual information (bits)')
dev.off()
```

## Mutual information for item response choices with actions factor
```{r}
Actions.df <- df_Items[, grep('Q1e|Q2e|Q3e', names(df_Items))]

Actions.MI.df <- MI.CI(Actions.df, scores$actions, reps = 100)

labels.list <- c('Q1E_1', 'Q1E_4', 'Q1E_13', 'Q2E_14', 'Q2E_6', 'Q3E_11', 
                 'Q3E_13', 'Q3E_20')

png('Figures/MutInfo_Actions.png')
ggplot(Actions.MI.df, aes(x = Prop.Sel, y = MI, color = Question, 
                          shape = Question)) +
  geom_point(size = 3.5, alpha = 0.25) +
  geom_errorbar(aes(ymin = CI.Low, ymax = CI.High), width = 0.01, size = 1, 
                alpha = 0.25) +
  geom_point(data = Actions.MI.df[Actions.MI.df[, 'Item'] %in% labels.list,], 
             aes(x = Prop.Sel, y = MI, color = Question), size = 3.5) +
  geom_errorbar(data = Actions.MI.df[Actions.MI.df[, 'Item'] %in% labels.list,], 
                aes(ymin = CI.Low, ymax = CI.High), width = 0.01, size = 0.8, 
                alpha = 1) +
  scale_shape_manual(values = c(15, 16, 17)) +
  scale_color_manual(values = c("#0072b2", "#d55e00", "#009e73")) +
  scale_fill_manual(values = labels.list) +
  geom_label_repel(data = subset(Actions.MI.df, Item %in% labels.list),
            aes(x = Prop.Sel, y = MI, color = Question, label = Item), 
            nudge_x = 0.04, nudge_y = 0.01, size = 6, show.legend = FALSE) +
  theme_classic() +
  theme(text = element_text(size = 18)) +
  labs(x = 'Fraction of times selected', y = 'Mutual information (bits)')
dev.off()
```

# Mutual information with vector of factor scores
```{r}
net.df <- MI.CI(df_Items, scores, reps = 100, vector = TRUE)

ggplot(net.df, aes(x = Prop.Sel, y = MI, color = Question, shape = Question)) +
  geom_point(size = 3.5) +
  geom_errorbar(aes(ymin = CI.Low, ymax = CI.High), width = 0.01, size = 1) +
  scale_shape_manual(values = c(15, 16, 17, 15, 16, 17, 15, 15, 17, 16)) +
  scale_color_manual(values = c(rep("#0072b2", 3), rep("#d55e00", 3),
                                rep("#009e73", 3), "#cc79a7")) #+
  # scale_fill_manual(values = labels.list) +
  # geom_label_repel(data = subset(Actions.MI.df, Item %in% labels.list),
  #           aes(x = Prop.Sel, y = MI, color = Question, label = Item), nudge_x = 0.04, 
  #           nudge_y = 0.01, size = 6, show.legend = FALSE) +
  # theme_classic() +
  # theme(text = element_text(size = 18)) +
  # labs(x = 'Fraction of times selected', y = 'Mutual information (bits)')
```

