---
output:
  html_document: default
  pdf_document: default
---
# Setup

## Load necessary packages
```{r, message = FALSE, warning = FALSE, echo = FALSE}
library(plyr)
library(readr)
library(tidyverse)
library(DescTools)
library(ryouready)
library(reshape2)
library(stringr)
library(ggthemes)
library(cluster)
library(factoextra)
library(DescTools)
theme_set(theme_fivethirtyeight())
```

## Load and combine students' responses
```{r, echo = FALSE}
files = list.files("C:/Users/Cole/Documents/DATA/PLIC_DATA/SurveysAugust2020/", 
                   recursive = TRUE, full.names = TRUE)

header = read.csv(files[1], header = F, nrows = 1, as.is = T)
df.students = ldply(files, read.csv, header = T, skip = 1) %>%
  `colnames<-`(header) %>%
  filter(V5 == 1) %>%
  filter((Qt1_3 > 30) | (Qt2_3 > 30) | (Qt3_3 > 30) | (Qt4_3 > 3))
df.students = df.students[df.students[, 'Unnamed: 7'] == 1,]
```

## Load experts file and do some preprocessing
```{r, echo = FALSE, results = FALSE}
file = 'C:/Users/Cole/Documents/DATA/PLIC_DATA/Experts/Experts_v08042020_09202020.csv'

# info data.frame from second row of file
info <- data.frame(lapply(read.csv(file, nrows = 1), 
                          FUN = function(x) gsub("^.*- ", "", x)))

# headers from first row
headers = read.csv(file, header = F, nrows = 1, as.is = T)
headers <- data.frame(lapply(headers, function(x) sub(' ', '.', x)))
df.experts = read.csv(file, header = F)
df.experts <- df.experts %>% # filtering
  tail(., nrow(df.experts) - 3) %>% # get rid of first three rows, no data there
  `colnames<-`(headers) %>%
  filter(Finished == 1) %>%
  filter((Qt1_Page.Submit > 30) | (Qt2_Page.Submit > 30) | 
           (Qt3_Page.Submit > 30) | (Qt4_Page.Submit > 30)) %>%
  filter(!(Q6a %in% c(1, 4))) # expertise filter

# check which entries to manually delete
df.experts[df.experts$Q6a %in% c(8, 9), c('Q6a', 'Q6a_8_TEXT')]
df.experts <- df.experts[!(row.names(df.experts) %in% c(4, 16)),]

# a bunch of recoding because we were not at all consistent within Qualtrics
df.experts <- recode2(df.experts, 
                      vars = colnames(df)[colnames(df) %like any% c('%Q139%',
                                                                    '%Q140%', 
                                                                    '%Q141%',
                                                                    '%Q157%')], 
                      recodes = "6 = 1; 7 = 2; 9 = 3; 10 = 4")
df.experts <- recode2(df.experts, vars = c('Q1a'), 
                      recodes = "1 = 1; 2 = 2; 3 = 4; 5 = 3")
df.experts <- recode2(df.experts, vars = c('Q133'), 
                      recodes = "1 = 1; 2 = 2; 5 = 3; 6 = 4")
```

## Combine and process students and experts data.frames
```{r, echo = FALSE}
common_cols <- intersect(colnames(df.students), colnames(df.experts))
df <- rbind(
  subset(df.students %>%
           mutate(Respondent = 'Student'), select = c(common_cols, 'Respondent')), 
  subset(df.experts %>%
           mutate(Respondent = 'Expert'), select = c(common_cols, 'Respondent'))
)

df <- recode2(df, vars = c('Q1a', 'Q2a', 'Q3a'), recodes = "1 = 'Support'; 
              2 = 'Refute'; 3 = 'Neither'; 4 = 'More evidence'")
df <- recode2(df, vars = c('Q133', 'Q144', 'Q148'), 
              recodes = "1 = 'Data collection'; 2 = 'Amount of data'; 
                          3 = 'Analysis'; 4 = 'Others'")
df <- recode2(df, vars = c('Q3c'), 
              recodes = "1 = 'fixed at zero'; 2 = 'not fixed at zero'; 
                          3 = 'other'")
df <- recode2(df, vars = c('Q4a'), 
              recodes = "1 = 'Group 1'; 2 = 'Group 2'; 3 = 'Both'; 4 = 'Neither'")
df <- recode2(df, vars = colnames(df)[colnames(df) %like any% c('%Q152%',
                                                                '%Q153%', 
                                                                '%Q154%')], 
              recodes = "1 = '1'; 2 = '2'; 3 = 'B'; 4 = 'N'")
df[is.na(df)] <- ''
```

# Analysis

## Raw distributions

### Page 1
```{r, echo = FALSE}
print('What do you think Group 1 should say about whether their data agree with 
      the model?')

ggplot(df, aes(x = factor(Q1a), fill = factor(Q1a))) +
  geom_bar() +
  ggtitle('Group 1, data agree with the model') +
  theme(legend.position = "none") +
  facet_wrap(~Respondent, scales = 'free_y') + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

print('Which statements below support your reasoning for whether Group 1s data 
      agree with the model?')

# get all columns for this multiple response questions
cols.temp <- colnames(df)[(colnames(df) %like% '%Q1b%') & 
                            !(colnames(df) %like% '%TEXT%')]

# melt to one column
df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(value = ifelse(value == 1, 1, 0))

# print info for each response
data.frame(t(info[, cols.temp]))

# normalize y-axis, so its fraction of experts...maybe I should add a label...?
ggplot(df.temp, aes(x = variable, fill = variable, y = value)) +
  geom_bar(stat = 'identity')  +
  ggtitle('Group 1, reasoning') +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 30, hjust = 1)) +
  facet_wrap(~Respondent, scales = 'free_y')

print('Group 1 evaluate methods')

cols.temp <- colnames(df)[(colnames(df) %like% '%Q139%') & 
                            !(colnames(df) %like% '%TEXT%')]

# we'll facet these Likert questions, so they're all in one plot
df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(variable = case_when(
    variable == 'Q139_1' ~ 'Equipment used',
    variable == 'Q139_2' ~ 'Variables measured',
    variable == 'Q139_3' ~ 'Variables controlled',
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(variable) & value != '')

ggplot(df.temp, aes(x = factor(value), fill = factor(value))) +
  geom_bar() +
  ggtitle('Group 1, data collection methods') +
  theme(legend.position = "none") +
  facet_grid(Respondent~variable, scales = 'free_y')

cols.temp <- colnames(df)[(colnames(df) %like% '%Q140%') & 
                            !(colnames(df) %like% '%TEXT%')]

df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(variable = case_when(
    variable == 'Q140_1' ~ 'N trials',
    variable == 'Q140_2' ~ 'N masses',
    variable == 'Q140_3' ~ 'N bounces',
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(variable) & value != '')

ggplot(df.temp, aes(x = factor(value), fill = factor(value))) +
  geom_bar() +
  ggtitle('Group 1, amount of data') +
  theme(legend.position = "none") +
  facet_wrap(Respondent~variable, scales = 'free_y')

cols.temp <- colnames(df)[(colnames(df) %like% '%Q141%') & 
                            !(colnames(df) %like% '%TEXT%')]

df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(variable = case_when(
    variable == 'Q141_1' ~ 'Explanations',
    variable == 'Q141_2' ~ 'Analysis',
    variable == 'Q141_3' ~ 'Similar k values',
    variable == 'Q141_4' ~ 'Uncertainty in data',
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(variable) & value != '')

ggplot(df.temp, aes(x = factor(value), fill = factor(value))) +
  geom_bar() +
  ggtitle('Group 1, analysis and outcomes') +
  theme(legend.position = "none") +
  facet_wrap(Respondent~variable, scales = 'free_y', ncol = 4)

print('How effective do you think Group 1s method was for testing whether the 
      data obey the model?')

ggplot(df, aes(x = factor(Q1c), fill = factor(Q1c))) +
  geom_bar() +
  ggtitle('Group 1, method effectiveness') +
  theme(legend.position = "none") +
  facet_wrap(~Respondent, scales = 'free_y')

print('What feature was most important to you in evaluating the effectiveness of 
      Group 1s methods (either as strengths or weaknesses)?')

ggplot(df, aes(x = factor(Q133), fill = factor(Q133))) +
  geom_bar() +
  ggtitle('Group 1, feature of method') +
  theme(legend.position = "none") +
  facet_wrap(~Respondent, scales = 'free_y') +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

print('What do you think Group 1 should do next?')

cols.temp <- colnames(df)[(colnames(df) %like% '%Q134%') & 
                            !(colnames(df) %like% '%TEXT%')]

df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(value = ifelse(value == 1, 1, 0))

data.frame(t(info[, cols.temp]))

ggplot(df.temp, aes(x = variable, fill = variable, y = value)) +
  geom_bar(stat = 'identity')  +
  ggtitle('Group 1, what to do next') +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 30, hjust = 1)) +
  facet_wrap(~Respondent, scales = 'free_y')
```

### Page 2
```{r, echo = FALSE}
print('What do you think Group 2 should say about whether their data agree with 
      the model?')

ggplot(df, aes(x = factor(Q2a), fill = factor(Q2a))) +
  geom_bar() +
  ggtitle('Group 1, data agree with the model') +
  theme(legend.position = "none") +
  facet_wrap(~Respondent, scales = 'free_y') + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

print('Which statements below support your reasoning for whether Group 2s data 
      agree with the model?')

# get all columns for this multiple response questions
cols.temp <- colnames(df)[(colnames(df) %like% '%Q2b%') & 
                            !(colnames(df) %like% '%TEXT%')]

# melt to one column
df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(value = ifelse(value == 1, 1, 0))

# print info for each response
data.frame(t(info[, cols.temp]))

# normalize y-axis, so its fraction of experts...maybe I should add a label...?
ggplot(df.temp, aes(x = variable, fill = variable, y = value)) +
  geom_bar(stat = 'identity')  +
  ggtitle('Group 2, reasoning') +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, vjust = 0.25)) +
  facet_wrap(~Respondent, scales = 'free_y')

print('Group 2 evaluate methods')

cols.temp <- colnames(df)[(colnames(df) %like% '%Q2d%') & 
                            !(colnames(df) %like% '%TEXT%')]

df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(variable = case_when(
    variable == 'Q2d_1' ~ 'Equipment used',
    variable == 'Q2d_2' ~ 'Variables measured',
    variable == 'Q2d_3' ~ 'Variables controlled',
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(variable) & value != '')

ggplot(df.temp, aes(x = factor(value), fill = factor(value))) +
  geom_bar() +
  ggtitle('Group 2, data collection methods') +
  theme(legend.position = "none") +
  facet_wrap(Respondent~variable, scales = 'free_y')

cols.temp <- colnames(df)[(colnames(df) %like% '%Q142%') & 
                            !(colnames(df) %like% '%TEXT%')]

df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(variable = case_when(
    variable == 'Q142_1' ~ 'N trials',
    variable == 'Q142_2' ~ 'N masses',
    variable == 'Q142_3' ~ 'N bounces',
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(variable) & value != '')

ggplot(df.temp, aes(x = factor(value), fill = factor(value))) +
  geom_bar() +
  ggtitle('Group 2, amount of data') +
  theme(legend.position = "none") +
  facet_wrap(Respondent~variable, scales = 'free_y')

cols.temp <- colnames(df)[(colnames(df) %like% '%Q157%') & 
                            !(colnames(df) %like% '%TEXT%')]

df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(variable = case_when(
    variable == 'Q157_1' ~ 'Explanations',
    variable == 'Q157_2' ~ 'Analysis',
    variable == 'Q157_3' ~ 'Similar k values',
    variable == 'Q157_4' ~ 'Uncertainty in data',
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(variable) & value != '')

ggplot(df.temp, aes(x = factor(value), fill = factor(value))) +
  geom_bar() +
  ggtitle('Group 2, analysis and outcomes') +
  theme(legend.position = "none") +
  facet_wrap(Respondent~variable, scales = 'free_y', ncol = 4)

print('How effective do you think Group 2s method was for testing whether the data 
      obey the model?')

ggplot(df, aes(x = factor(Q2c), fill = factor(Q2c))) +
  geom_bar() +
  ggtitle('Group 2, method effectiveness') +
  theme(legend.position = "none") +
  facet_wrap(~Respondent, scales = 'free_y')

print('What feature was most important to you in evaluating the effectiveness of 
      Group 2s methods (either as strengths or weaknesses)?')

ggplot(df, aes(x = factor(Q144), fill = factor(Q144))) +
  geom_bar() +
  ggtitle('Group 2, feature of method') +
  theme(legend.position = "none") +
  facet_wrap(~Respondent, scales = 'free_y') +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

print('What do you think Group 2 should do next?')

cols.temp <- colnames(df)[(colnames(df) %like% '%Q2e%') & 
                            !(colnames(df) %like% '%TEXT%')]

df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(value = ifelse(value == 1, 1, 0))

data.frame(t(info[, cols.temp]))

ggplot(df.temp, aes(x = variable, fill = variable, y = value)) +
  geom_bar(stat = 'identity')  +
  ggtitle('Group 2, what to do next') +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 30, hjust = 1)) +
  facet_wrap(~Respondent, scales = 'free_y')
```

### Page 3
```{r, echo = FALSE}
print('What do you think Group 2 should say about whether their data agree with 
      the model?')

ggplot(df, aes(x = factor(Q3a), fill = factor(Q3a))) +
  geom_bar() +
  ggtitle('Group 2, data agree with the model') +
  theme(legend.position = "none") +
  facet_wrap(~Respondent, scales = 'free_y') + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

print('Which statements below support your reasoning for whether Group 2s data 
      agree with the model?')

cols.temp <- colnames(df)[(colnames(df) %like% '%Q145%') & 
                            !(colnames(df) %like% '%TEXT%')]

df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(value = ifelse(value == 1, 1, 0))

data.frame(t(info[, cols.temp]))

ggplot(df.temp, aes(x = variable, fill = variable, y = value)) +
  geom_bar(stat = 'identity')  +
  ggtitle('Group 2, reasoning') +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, vjust = 0.25)) +
  facet_wrap(~Respondent, scales = 'free_y')

print('Which fit do you think Group 2 should use?')

ggplot(df, aes(x = factor(Q3c), fill = factor(Q3c))) +
  geom_bar() +
  ggtitle('Group 2, which fit') +
  theme(axis.text.x = element_text(angle = 30, hjust = 1),
        legend.position = "none") +
  facet_wrap(~Respondent, scales = 'free_y')

print('Which items below best reflect your reasoning?')

cols.temp <- colnames(df)[(colnames(df) %like% '%Q3d%') & 
                            !(colnames(df) %like% '%TEXT%')]

df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(value = ifelse(value == 1, 1, 0))

data.frame(t(info[, cols.temp]))

ggplot(df.temp, aes(x = variable, fill = variable, y = value)) +
  geom_bar(stat = 'identity')  +
  ggtitle('Group 2, reasoning for fit') +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 30, hjust = 1)) +
  facet_wrap(~Respondent, scales = 'free_y')

print('What do you think Group 2 should do next?')

cols.temp <- colnames(df)[(colnames(df) %like% '%Q147%') & 
                            !(colnames(df) %like% '%TEXT%')]

df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(value = ifelse(value == 1, 1, 0))

data.frame(t(info[, cols.temp]))

ggplot(df.temp, aes(x = variable, fill = variable, y = value)) +
  geom_bar(stat = 'identity')  +
  ggtitle('Group 2, what to do next') +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 30, hjust = 1)) +
  facet_wrap(~Respondent, scales = 'free_y')
```

### Page 4
```{r, echo = FALSE}
print('Which group do you think did a better job of testing the model?')

ggplot(df, aes(x = factor(Q4a), fill = factor(Q4a))) +
  geom_bar() +
  ggtitle('Which group did a better job?') +
  theme(legend.position = "none") +
  facet_wrap(~Respondent, scales = 'free_y')

print('Compare methods')

cols.temp <- colnames(df)[(colnames(df) %like% '%152%') & 
                            !(colnames(df) %like% '%TEXT%')]

df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(variable = case_when(
    variable == 'Q152_1' ~ 'Equipment used',
    variable == 'Q152_2' ~ 'Variables measured',
    variable == 'Q152_3' ~ 'Variables controlled',
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(variable) & value != '')

ggplot(df.temp, aes(x = factor(value), fill = factor(value))) +
  geom_bar() +
  ggtitle('Compare data collection methods') +
  theme(legend.position = "none") +
  facet_wrap(Respondent~variable, scales = 'free_y')

cols.temp <- colnames(df)[(colnames(df) %like% '%Q153%') & 
                            !(colnames(df) %like% '%TEXT%')]

df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(variable = case_when(
    variable == 'Q153_1' ~ 'N trials',
    variable == 'Q153_2' ~ 'N masses',
    variable == 'Q153_3' ~ 'N bounces',
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(variable) & value != '')

ggplot(df.temp, aes(x = factor(value), fill = factor(value))) +
  geom_bar() +
  ggtitle('Compare amount of data') +
  theme(legend.position = "none") +
  facet_wrap(Respondent~variable, scales = 'free_y')

cols.temp <- colnames(df)[(colnames(df) %like% '%Q154%') & 
                            !(colnames(df) %like% '%TEXT%')]

df.temp <- df[, c(cols.temp, 'Respondent')] %>%
  melt(., measure.vars = cols.temp) %>%
  mutate(variable = case_when(
    variable == 'Q154_1' ~ 'Explanations',
    variable == 'Q154_2' ~ 'Analysis',
    variable == 'Q154_3' ~ 'Similar k values',
    variable == 'Q154_4' ~ 'Uncertainty in data',
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(variable) & value != '')

ggplot(df.temp, aes(x = factor(value), fill = factor(value))) +
  geom_bar() +
  ggtitle('Compare analysis and outcomes') +
  theme(legend.position = "none") +
  facet_wrap(Respondent~variable, scales = 'free_y', ncol = 4)

print('What feature was most important to you for comparing the two groups?')

ggplot(df, aes(x = factor(Q148), fill = factor(Q148))) +
  geom_bar() +
  ggtitle('Feature for comparing methods') +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 30, hjust = 1)) +
  facet_wrap(~Respondent, scales = 'free_y')
```

## Evaluate isolated versus comparison questions

### Raw bins
```{r, echo = FALSE, warning = FALSE, message = FALSE}
theme_set(theme_gdocs())
Group.compare.scatter <- function(df, Group1, Group2, Compare, Question){
  df.temp <- df[, c(Group1, Group2, Compare)]
  colnames(df.temp) <- c('Group.1', 'Group.2', 'Comparison')
  df.temp$Group.1 <- as.numeric(df.temp$Group.1)
  df.temp$Group.2 <- as.numeric(df.temp$Group.2)

  df.summary <- df.temp %>%
    filter(!is.na(Group.1) & !is.na(Group.2) & (Comparison != '')) %>%
    group_by(Group.1, Group.2, Comparison) %>%
    summarize(N = n())

  df.summary$Group.1 <- df.summary$Group.1 - 
    0.1 * (df.summary$Comparison %in% c('1', 'B')) + 
    0.1 * (df.summary$Comparison %in% c('2', 'N'))
  df.summary$Group.2 <- df.summary$Group.2 - 
    0.1 * (df.summary$Comparison %in% c('B', 'N')) + 
    0.1 * (df.summary$Comparison %in% c('1', '2'))

  print(ggplot(df.summary, aes(x = Group.1, y = Group.2, color = Comparison, 
                               size = N)) +
          geom_point() +
          scale_size_area() +
          labs(x = 'Group 1', y = 'Group 2', title = Question))

}

df.students = df[df$Respondent == 'Student',]
Group.compare.scatter(df.students, 'Q139_1', 'Q2d_1', 'Q152_1', 'Equipment used')
Group.compare.scatter(df.students, 'Q139_2', 'Q2d_2', 'Q152_2', 
                      'Variables measured')
Group.compare.scatter(df.students, 'Q139_3', 'Q2d_3', 'Q152_3', 
                      'Variables controlled')

Group.compare.scatter(df.students, 'Q140_1', 'Q142_1', 'Q153_1', 'N trials')
Group.compare.scatter(df.students, 'Q140_2', 'Q142_2', 'Q153_2', 'N masses')
Group.compare.scatter(df.students, 'Q140_3', 'Q142_3', 'Q153_3', 'N bounces')

Group.compare.scatter(df.students, 'Q141_1', 'Q157_1', 'Q154_1', 'Explanations')
Group.compare.scatter(df.students, 'Q141_2', 'Q157_2', 'Q154_2', 'Analysis')
Group.compare.scatter(df.students, 'Q141_3', 'Q157_3', 'Q154_3', 
                      'Similar k values')
Group.compare.scatter(df.students, 'Q141_4', 'Q157_4', 'Q154_4', 
                      'Uncertainty in data')
```

### Evaluate clusters
```{r, echo = FALSE, warning = FALSE, message = FALSE}
df.cluster <- df.students[, c('Q139_1', 'Q2d_1', 'Q139_2', 'Q2d_2', 'Q139_3', 
                              'Q2d_3', 'Q140_1', 'Q142_1', 'Q140_2', 'Q142_2', 
                              'Q140_3', 'Q142_3', 'Q141_1', 'Q157_1', 'Q141_2', 
                              'Q157_2', 'Q141_3', 'Q157_3', 'Q141_4', 'Q157_4')]

df.cluster <- data.frame(lapply(df.cluster, as.numeric))
df.cluster <- na.omit(df.cluster)

set.seed(11)

fviz_nbclust(df.cluster, kmeans, method = "silhouette")
final <- kmeans(df.cluster, 2, nstart = 11)
print('Cluster centers and difference between centers')
print(final$centers)
print(diff(as.matrix(final$centers)))

fviz_cluster(final, data = df.cluster)
```

#### Selections by cluster
```{r, echo = FALSE, warning = FALSE, message = FALSE}
df.clusters <- right_join(data.frame(df.students, names = rownames(df.students)), 
                          data.frame(final$cluster, 
                                     names = names(final$cluster))) %>%
  select(final.cluster, Q152_1, Q152_2, Q152_3, Q153_1, Q153_2, Q153_3, Q154_1, 
         Q154_2, Q154_3, Q154_4) %>%
  melt(., id.vars = 'final.cluster')

ggplot(df.clusters, aes(x = final.cluster, fill = as.factor(value))) +
  geom_bar() +
  facet_wrap(~variable, scales = 'free_x') +
  scale_x_continuous(breaks = c(1, 2), labels = c('1', '2')) +
  labs(x = 'Cluster', fill = 'Comparison')
```

### Associations (Cramer's V, uncorrected) between items
```{r, echo = FALSE}
df.cors <- lapply(inner_join(data.frame(df.cluster, names = rownames(df.cluster)),
                             data.frame(df.students[, c('Q152_1', 'Q152_2', 
                                                        'Q152_3', 'Q153_1', 
                                                        'Q153_2', 'Q153_3', 
                                                        'Q154_1', 'Q154_2', 
                                                        'Q154_3', 'Q154_4')], 
                                        names = rownames(df.students))), 
                  as.factor) %>%
  data.frame(.) %>%
  dplyr::select(-names)

cor.matrix <- round(PairApply(df.cors, FUN = CramerV), 2)
melted.cor.matrix <- melt(cor.matrix)

ggplot(data = melted.cor.matrix, aes(x = Var1, y = Var2, fill = value)) + 
  geom_tile() +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(0,1)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.25))
```

#### Fractions of selections by combination
```{r, echo = FALSE, warning = FALSE, message = FALSE}
df.students[df.students == ''] <- NA_character_

df.students[, c('Q152_1', 'Q152_2', 'Q152_3', 'Q153_1', 'Q153_2', 'Q153_3', 
                'Q154_1', 'Q154_2', 'Q154_3', 'Q154_4')] %>%
  na.omit(.) %>%
  group_by_all() %>%
  summarize(frac = n()/nrow(df.students)) %>%
  arrange(desc(frac)) %>%
  head(10)
```



