---
output:
  pdf_document: default
  html_document: default
---
# Load necessary packages
```{r, results = 'hide', message = FALSE, warning = FALSE}
library(easypackages)
libraries('tidyverse', 'data.table', 'reshape2', 'ggpubr', 'lmerTest', 'reghelper', 'car',
          'lattice', 'sjstats', 'sjPlot', 'gridExtra', 'stargazer', 'lavaan', 'semPlot',
          'psych')
theme_set(theme_classic(base_size = 14)) # set font size for ggplot
```

# Scoring/cleaning functions
```{r}
Read.Score <- function(file){
  # read master E-CLASS file and calculate total scores on student and expert questions
  dt <- fread(file)
  
  # columns with students responses end in a (student Qs) or b (expert Qs)...get those
  answers.cols <- names(dt)[grep('(a|b)$', names(dt))]
  
  # correct answers marked as 5, incorrect as 1, and neutral as 0...map to +/- 1 and 0
  dt[, (answers.cols) := lapply(.SD, function(x) case_when(x == 5 ~ 1,
                                                           x == 1 ~ -1,
                                                           TRUE ~ 0)),
     .SDcols = answers.cols]
  df <- dt[, -c('q40a', 'q40b')] # q40 was a filter question, no part of scoring

  # sum student/expert scores
  df$student.score <- rowSums(df %>% select(grep("a$", names(.))))
  df$expert.score <- rowSums(df %>% select(grep("b$", names(.))))
  
  return(df)
}
```

# Read, score, and match
```{r}
# read course information survey (CIS) and pre/post survey data
cis.df <- read.csv('C:/Users/Cole/Documents/GRA_Summer2020/eclass-public-analysis/anon_cis_CW.csv')
pre.df <- Read.Score('C:/Users/Cole/Documents/GRA_Summer2020/eclass-public-analysis/anon_pre.csv')

# join CIS on presurvey
cis.pre.df <- right_join(cis.df, pre.df, by = c('pre_survey_id' = 'survey_id'), 
                         suffix = c('.CIS', '.pre'))
post.df <- Read.Score('C:/Users/Cole/Documents/GRA_Summer2020/eclass-public-analysis/anon_post.csv')

# join presurveys (with CIS) on postsurveys...full join keeps unmatched surveys
full.df <- full_join(cis.pre.df, post.df, by = c('post_survey_id' = 'survey_id', 
                                                 'anon_student_id'), 
                     suffix = c('.pre', '.post'))

# mutate lab type and course level info from CIS
full.df <- full.df %>%
    mutate(Lab.type = case_when(
      Q33 == 'Reinforce physics concepts.' ~ 'Concepts-based',
      Q33 == 'Both about equally.' ~ 'Mixed',
      Q33 == 'Develop lab skills.' ~ 'Skills-based',
      TRUE ~ NA_character_
    ), 
    Course.level = case_when(
      Q18 == 'Beyond the first year lab' ~ 'BFY',
      Q27 == 'Calculus-based' ~ 'FY.Calc',
      Q27 == 'Algebra-based' ~ 'FY.Alg',
      TRUE ~ NA_character_
    ))

full.df <- data.table(full.df)[, `:=`(N.students = .N, 
                                      pre.rate = sum(!is.na(student.score.pre))/.N,
                                      post.rate = sum(!is.na(student.score.post))/.N), 
                               .(ResponseId.CIS)] %>%
  data.frame()

# remove whole classes without type and/or level information
complete.df <- full.df %>%
  filter(!is.na(Lab.type) & !is.na(Course.level) & (pre.rate > 0) & (post.rate > 0))

# get matched dataset
df.matched <- complete.df %>%
  filter(!is.na(student.score.pre) & !is.na(student.score.post))

data.frame(N.student.records = unlist(lapply(list(full.df, complete.df, df.matched), 
                                             function(x) nrow(x))),
           N.students = unlist(lapply(list(full.df, complete.df, df.matched), 
                                      function(x) length(unique(x[, 
                                                                  'anon_student_id'])))),
           N.classes = unlist(lapply(list(full.df, complete.df, df.matched), 
                                     function(x) length(unique(x[, 'ResponseId.CIS'])))),
           N.institutions = unlist(lapply(list(full.df, complete.df, df.matched),
                                          function(x) length(unique(x[,
                                                                      'anon_university_id'])))), row.names = c('full dataset', 'course info', 'matched'))

# Breakdown of institution type, course level, and lab type
table(df.matched[!duplicated(df.matched$anon_university_id),]$Q15, exclude = NULL)
table(df.matched[!duplicated(df.matched$ResponseId.CIS),]$Course.level, exclude = NULL)
table(df.matched[!duplicated(df.matched$ResponseId.CIS),]$Lab.type, exclude = NULL)
```

# Data processing
```{r}
# replace declared major with intended major in cases where students intend to switch
df.matched[is.na(df.matched$Q48) | (df.matched$Q48 == 0),
'Q48'] <- df.matched[is.na(df.matched$Q48) | (df.matched$Q48 == 0), 'Q47']

# mutate and combine categories
df.matched <- df.matched %>%
  mutate(Major = case_when(
    Q48 == 1 ~ 'Physics',
    Q48 == 2 ~ 'Chemistry',
    Q48 == 3 ~ 'Biochemistry',
    Q48 == 4 ~ 'Biology',
    Q48 == 5 ~ 'Engineering',
    Q48 == 6 ~ 'Engineering Physics',
    Q48 == 7 ~ 'Astronomy',
    Q48 == 8 ~ 'Astrophysics',
    Q48 == 9 ~ 'Geology/geophysics',
    Q48 == 10 ~ 'Math/applied math',
    Q48 == 11 ~ 'Computer science',
    Q48 == 12 ~ 'Physiology',
    Q48 == 13 ~ 'Other science',
    Q48 == 14 ~ 'Non-science',
    Q48 == 15 ~ 'Open/undeclared',
    TRUE ~ 'Unknown'
  ),
  Gender = case_when(
    Q54 == 1 ~ 'Woman',
    Q54 == 2 ~ 'Man',
    Q54 == 3 ~ 'Other',
    TRUE ~ 'Unknown'
  )) %>%
  mutate(Major = case_when(
    (Major == 'Physics') | (Major == 'Engineering Physics') | (Major == 'Astronomy') | 
      (Major == 'Astrophysics') ~ 'Physics',
    (Major == 'Chemistry') | (Major == 'Biochemistry') | (Major == 'Biology') | 
      (Major == 'Physiology') ~ 'Chem.LifeSci',
    Major == 'Engineering' ~ 'Engineering',
    (Major == 'Math/applied math') | (Major == 'Computer science') ~ 'Math.CS',
    (Major == 'Geology/geophysics') | (Major == 'Other science') ~ 'OtherSci',
    Major == 'Non-science' ~ 'NonSci',
    Major == 'Open/undeclared' ~ 'Undeclared',
    Major == 'Unknown' ~ 'Unknown',
    TRUE ~ NA_character_
  )) %>% # set reference levels for factors...important for regressions
  mutate(Major = relevel(as.factor(Major), ref = 'Physics'),
         Gender = relevel(as.factor(Gender), ref = 'Man'),
         Lab.type = relevel(as.factor(Lab.type), ref = 'Concepts-based'),
         Course.level = relevel(as.factor(Course.level), ref = 'FY.Alg'))

# rename race columns
new.race.cols <- c('Race.ethnicity.Other', 'Race.ethnicity.Black', 
                 'Race.ethnicity.Hispanic', 'Race.ethnicity.Asian', 
                 'Race.ethnicity.White', 'Race.ethnicity.Unknown', 'Race.ethnicity.AmInd',
                 'Race.ethnicity.NatHawaii')
setnames(df.matched, old = c('Q52_7', 'Q52_3', 'Q52_4', 'Q52_2', 'Q52_6', 
                             'race_unknown', 'Q52_5', 'Q52_1'), new = new.race.cols)

# fill all NAs with zero and set factors to binary
df.matched[is.na(df.matched)] <- 0
df.matched[new.race.cols] <- lapply(df.matched[new.race.cols], factor, levels = c(0, 1))
```

# Demographic breakdowns
```{r}
Race.ethnicity.cols <- names(df.matched)[names(df.matched) %like% 'Race']
Race.ethnicity.table <- function(df, Lab.type = FALSE){
  # race/ethnicity variables are not independent...this function calculates tables for 
  # each of those variables
  if(Lab.type){
    for(col in Race.ethnicity.cols){
      print(col)
      print(table(df[, col], df$Lab.type))
    }
  } else {
    for(col in Race.ethnicity.cols){
      print(col)
      print(table(df[, col]))
    }
  }
}

# get demographic breakdowns across lab type
table(df.matched$Gender)
Race.ethnicity.table(df.matched)
table(df.matched$Lab.goal)
table(df.matched$Gender, df.matched$Lab.type)
Race.ethnicity.table(df.matched, Lab.type = TRUE)
```

# Descriptive statistics
```{r}
plot.pre.post <- function(df, var){
  # plot pre-post score shifts on overall student scores
  if(var == 'Race.ethnicity'){
    # race/ethnicity variables aren't independent, so we melt twice...first to put 
    # pre-post scores in long form
    df.long <- reshape2::melt(df.matched, id.vars = new.race.cols, 
                              measure.vars = c('student.score.pre', 'student.score.post'),
                              variable.name = 'Time', value.name = 'Score') %>%
      # ...then again to put race/ethnicity in long form
      reshape2::melt(., measure.vars = new.race.cols, 
                     id.vars = c('Time', 'Score'), variable.name = 'Race.ethnicity') %>%
      filter(value == 1) %>%
      select(Time, Score, Race.ethnicity) %>%
      rowwise() %>% # rowwise split the characters in the column to get nice tick labels
      mutate(Race.ethnicity = strsplit(as.character(Race.ethnicity), '\\.')[[1]][3])
    
  } else {
    # we only need to put the scores in long form since the gender/lab type variables are 
    # already long
    df.long <- reshape2::melt(df, measure.vars = c('student.score.pre',
                                                   'student.score.post'), 
                              variable.name = 'Time', value.name = 'Score')
  }
  
  p <- ggplot(df.long, aes_string(x = var, y = 'Score', group = 'Time', color = 'Time'))
  add_summary(p, fun = 'mean_se', group = c('Time')) +
    scale_color_manual(labels = c('pre', 'post'), values = c('#2271B2', '#D55E00')) +
    theme(axis.text.x = element_text(angle = 90))
}

plot.pre.post(df.matched, 'Gender')
plot.pre.post(df.matched, 'Race.ethnicity')
plot.pre.post(df.matched, 'Lab.type')
```

# Mixed-effects models
```{r}
# fit null model with random intercepts for class and institution 
# this model measures the interclass correlation coefficient (ICC)
mod0 <- lmer(student.score.post ~ (1 | anon_university_id/ResponseId.CIS), df.matched)
r2(mod0)

# fit model of interest
mod <- lmer(student.score.post ~ student.score.pre + Course.level + Lab.type * 
               (Gender + Race.ethnicity.AmInd + Race.ethnicity.NatHawaii + 
               Race.ethnicity.Other + Race.ethnicity.Black + Race.ethnicity.Hispanic + 
               Race.ethnicity.Asian + Race.ethnicity.White + Race.ethnicity.Unknown) + 
               Major + (1 | anon_university_id/ResponseId.CIS), df.matched)
summary(mod)

# get standardized coefficients, grand-mean-centering continuous variables
noStandard.cols <- c('Lab.type', 'Course.level', 'Major', 'Gender', 
                     names(df.matched)[names(df.matched) %like% "Race"])
class(mod) <- "lmerMod"
mod.std <- beta(mod, skip = noStandard.cols)
```

# Variance inflation factors and model diagnostics
```{r}
# variance inflation factors...ratio of variance in measured parameter compared to model 
# with only that parameter
vif(mod)
# fitted values versus residuals...should be no trend
plot(mod, xlab = 'Fitted values', ylab = 'Residuals')
qqmath(mod) # standardized residuals versus standard quantiles
```

# Output stargazer
```{r, results = 'hide', message = FALSE, warning = FALSE, include = FALSE}
# standardized model appended .z to this column, so we remove the appendix
rownames(mod.std$coefficients)[2] <- 'student.score.pre'

# coefficient labels
labels = c("Constant", "Pretest", "Beyond-first-year", "First-year (calculus)", "Mixed", 
           "Skills-based", "Non-binary", "Unknown", "Woman", "American Indian", 
           "Native Hawaiian", "Other", "Black", "Hispanic", "Asian", "White", "Unknown", 
           "LifeSci/Chem", "Engineering", "Math/CS", "Non-science", "Other science", 
           "Undeclared", "Unknown", "Mixed * Non-binary", "Skills-based * Non-binary", 
           "Mixed * Unknown", "Skills-based * Unknown", "Mixed * Woman", 
           "Skills-based * Woman", "Mixed * American Indian", 
           "Skills-based * American Indian", "Mixed * Native Hawaiian", 
           "Skills-based * Native Hawaiian", "Mixed * Other",  "Skills-based * Other", 
           "Mixed * Black", "Skills-based * Black", "Mixed * Hispanic", 
           "Skills-based * Hispanic", "Mixed * Asian", "Skills-based * Asian", 
           "Mixed * White", "Skills-based * White", "Mixed * Unknown", 
           "Skills-based * Unknown")

# concatenate estimates and SEs from raw and standardized models
stargazer(mod, mod, mod, mod, coef = list(summary(mod)$coefficients[, 1],
                                          summary(mod)$coefficients[, 2], 
                                          mod.std$coefficients[, 1],
                                          mod.std$coefficients[, 2]), 
          se = list(summary(mod)$coefficients[, 2], NA, mod.std$coefficients[, 2], NA), 
          type = 'latex', intercept.bottom = FALSE, style = 'asr', keep.stat = c(''), 
          column.labels = c('Beta', 'SE', 'Beta.std', 'SE'), model.numbers = FALSE, 
          covariate.labels = labels, dep.var.labels = 'E-CLASS posttest scores', 
          out ='E-CLASS_model.tex')
```

# Marginal effects plots
```{r}
# marginal effects (average effect) of different labs on posttest scores
png('Figures/E-CLASS_Labtype.png', width = 586, height = 726)
p1 <- plot_model(mod, type = 'eff', terms = c('Lab.type'), dot.size = 4, line.size = 1, 
                 ci.lvl = 0.67, title = '', 
                 axis.title = 'Predicted E-CLASS posttest scores', 
                 colors = c('#e69f00', '#009e74', '#0071b2'), dodge = 0.5) +
  theme(legend.position = 'right',
        text = element_text(size = 25)) +
  xlab('')
p1
dev.off()
p1$data

# average over lab type and gender
p2 <- plot_model(mod, type = 'eff', terms = c('Gender', 'Lab.type'), dot.size = 4, 
                 line.size = 1, ci.lvl = 0.67, title = '', 
                 axis.title = 'Predicted E-CLASS posttest scores', 
                 colors = c('#e69f00', '#009e74', '#0071b2'), dodge = 0.5) +
  scale_x_discrete(limits = c("Man", "Non-binary", "Woman", "Unknown")) +
  labs(color = 'Lab type')

p2.new <- p2
p2.new$data$x <- rep(c(1, 2, 4, 3), 3)
```

# Race/ethnicity marginal effects plots
```{r}
# average over lab type and race/ethnicity...since race/ethnicity variables are not 
# independent, we calculate marginal effects separately for each variable...
p3.native <- plot_model(mod, type = 'eff', terms = c('Race.ethnicity.Other [1]', 
                                                      'Lab.type')) 
# the [1]s are because effects are estimated for variable = 0 and variable = 1...we only 
# want the 1s
df.race.eff <- data.frame(p3.native$data) %>%
  mutate(race.ethnicity = 'Race.ethnicity.Other')
for(race in c(new.race.cols[2:length(new.race.cols)])){
  p3 <- plot_model(mod, type = 'eff', terms = c(paste(race, ' [1]', sep = ''),
                                                 'Lab.type'))
  # ...bind results in one dataframe...
  df.race.eff <- rbind(df.race.eff, data.frame(p3$data) %>%
                         mutate(race.ethnicity = race))
}

# ...and clean up the dataframe a little bit
df.race.eff <- df.race.eff %>%
  mutate(group = factor(group, levels = c('Concepts-based', 'Mixed', 'Skills-based'),
                        ordered = TRUE)) %>%
  rowwise() %>%
  mutate(race.ethnicity = strsplit(race.ethnicity, '\\.')[[1]][3])
```

# Combine gender and race/ethnicity plots
```{r}
# add a var column to df.race.eff that is equal to 'Race/ethnicity'
df.race.eff <- df.race.eff %>%
  mutate(race.ethnicity = case_when(
    race.ethnicity == 'AmInd' ~ 'American Indian',
    race.ethnicity == 'NatHawaii' ~ 'Native Hawaiian',
    TRUE ~ race.ethnicity
  ),
  var = 'Race/ethnicity')

# get df.gender from marginal effects plot data...here the var is Gender
df.gender <- data.frame(p2.new$data) %>%
  mutate(gender = case_when(
    x == 1 ~ 'Man',
    x == 2 ~ 'Non-binary',
    x == 3 ~ 'Woman',
    x == 4 ~ 'Unknown'
  ),
  var = 'Gender')

# make sure the column names for both of the above dataframes are equal and combine them
cols <- c('x', 'predicted', 'std.error', 'conf.low', 'conf.high', 'lab', 'group', 'var')
colnames(df.race.eff) <- cols
colnames(df.gender) <- cols
df.demos <- rbind(df.race.eff, df.gender)

# plot combined gender and race/ethnicity marginal effects across lab type
png('Figures/E-CLASS_Labtype_Demos.png', width = 1172, height = 726)
ggplot(df.demos, aes(x = factor(group, levels = c('Man', 'Non-binary', 'Woman', 
                                                  'American Indian', 'Asian', 'Black',  
                                                  'Hispanic', 'Native Hawaiian', 'White', 
                                                  'Other', 'Unknown')), y = predicted, 
                     group = lab, color = lab)) +
  geom_point(size = 4, position = position_dodge(width = 0.7)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), size = 1, width = 0.2,
                position = position_dodge(width = 0.7)) +
  scale_color_manual(values = c('#e69f00', '#009e74', '#0071b2')) +
  labs(x = '', y = 'Predicted E-CLASS posttest scores', color = 'Lab type') +
  facet_wrap(~var, scales = 'free_x') +
  theme(legend.position = 'top') +
  theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust = 1),
        text = element_text(size = 20))
dev.off()
```

***Add comments after here**

# Combine E-CLASS and PLIC CIS datasets
```{r}
full.df <- fread('C:/Users/Cole/Documents/PLIC_DATA/Collective_Surveys/Complete/Complete_Concat_CourseInfo.csv') %>%
  filter(Survey_x == 'C' | Survey_y == 'C')

full.df[full.df$Survey_x == 'F', 'PreScores'] <- NA_real_
full.df[full.df$Survey_y == 'F', 'PostScores'] <- NA_real_

full.df <- data.table(full.df)[, `:=`(N.students = .N, pre.rate = sum(Survey_x == 'C')/.N,
                                      post.rate = sum(Survey_y == 'C')/.N),  .(Class_ID)]

full.df <- full.df %>%
  filter(!is.na(Lab_level) & !is.na(Lab_purpose) & (Lab_purpose != '') & (pre.rate > 0) & 
           (post.rate > 0))

df.PLIC <- full.df %>%
  filter(!is.na(PreScores) & !is.na(PostScores))

source('C:/Users/Cole/Documents/GitHub/PLIC/Process-Merge-Concat/PLIC_DataProcessing.R')
df.PLIC <- Collapse.vars(df.PLIC) %>%
  mutate(Lab_level = relevel(as.factor(case_when(
    Lab_level == 'Intro-Algebra' ~ 'FY-Algebra',
    Lab_level == 'Intro-Calculus' ~ 'FY-Calculus',
    (Lab_level == 'Sophomore') | (Lab_level == 'Junior') | 
      (Lab_level == 'Senior') ~ 'BFY',
    TRUE ~ NA_character_
  )), ref= 'FY-Algebra'),
  Lab_purpose = relevel(as.factor(case_when(
    Lab_purpose == 'Reinforce concepts' ~ 'Concepts-based',
    Lab_purpose == 'Both about equally' ~ 'Mixed',
    Lab_purpose == 'Develop lab skills' ~ 'Skills-based')), ref = 'Concepts-based'))

cols <- c('Class_ID', 'institution', 'Lab_purpose', 'T1', 'T2', 'T3', 'D1', 'D2', 'D3', 
          'D4', 'D5', 'E1', 'E2', 'E3', 'E4', 'E5', 'D6')

df.PLIC <- df.PLIC[, c('Class_ID', 'anon_institution_id', 'Lab_purpose', 'Q28_1', 
                       'Q28_2', 'Q28_3', 'Q29_1', 'Q29_2', 'Q29_3', 'Q29_4', 'Q29_5', 
                       'Q31_1', 'Q31_2', 'Q31_3', 'Q31_4', 'Q31_5', 'Q31_6', 'PreScores', 
                       'PostScores')]
colnames(df.PLIC) <- c(cols, 'PLIC.PreScores', 'PLIC.PostScores')

df.matched[, names(df.matched) %like% "Q34|Q35|Q36"] <- 
  data.frame(lapply(df.matched[, names(df.matched) %like% "Q34|Q35|Q36"], function(x) 
    droplevels(factor(as.vector(x), levels = c('Never', 'Rarely', 'Sometimes', 'Often', 
                                               'Always'), ordered = TRUE))))

df.matched[, names(df.matched) %like% "Q34|Q35|Q36"] <- data.frame(lapply(df.matched[, names(df.matched) %like% "Q34|Q35|Q36"], function(x) as.numeric(x)))

df.ECLASS <- df.matched[, c('ResponseId.CIS', 'anon_university_id', 'Lab.goal', 'Q34_1', 
                            'Q34_2', 'Q34_3', 'Q35_1', 'Q35_2', 'Q35_3', 'Q35_4', 
                            'Q35_5', 'Q36_1', 'Q36_2', 'Q36_3', 'Q36_4', 'Q36_5', 
                            'Q36_6', 'student.score.pre', 'student.score.post')]

colnames(df.ECLASS) <- c(cols, 'ECLASS.PreScores', 'ECLASS.PostScores')

df <- bind_rows(df.PLIC, df.ECLASS)

CIS.df <- unique(df[, cols[4:length(cols)]])

sum(do.call(paste0, CIS.df) %in% do.call(paste0, df.ECLASS[, cols[4:length(cols)]]))

sum(do.call(paste0, CIS.df) %in% do.call(paste0, df.PLIC[, cols[4:length(cols)]]))

sum(do.call(paste0, CIS.df) %in% do.call(paste0, df.ECLASS[, cols[4:length(cols)]]) & 
      do.call(paste0, CIS.df) %in% do.call(paste0, df.PLIC[, cols[4:length(cols)]]))
```

# Run CFA on CIS
```{r}
mod <- '
  decision =~ D1 + D2 + D3 + D4 + D5 + D6
  #epistemic =~ E1 + E2 + E3 + E4 + E5 + T1 + T2 + T3

  #decision ~~ epistemic
  #E1 ~~ E2 + E3
  #E4 ~~ E2 + E3
'

#fit <- cfa(mod, df[!duplicated(df$Class_ID),])
fit <- cfa(mod, CIS.df)
summary(fit, standardized = TRUE, fit.measures = TRUE, modindices = TRUE)
semPaths(fit, whatLabels = 'std', edge.color = 'black', curve = 2, residuals = FALSE, 
         label.scale = TRUE, mar = c(8, 8, 8, 8))
resid(fit, type = 'cor')
```

# Run EFA on half of the dataset
```{r}
set.seed(11)
inds <- sample(seq_len(nrow(CIS.df)), size = nrow(CIS.df)/2)
CIS.train.df <- CIS.df[inds,]

CIS.train.df

fa.parallel(CIS.train.df[, c('D1' , 'D2', 'D3', 'D4', 'D5', 'D6')])

fit1 <- fa(CIS.train.df[, c('D1' , 'D2', 'D3', 'D4', 'D5', 'D6')], 1)
fit1
fa.diagram(fit1)

fit3 <- fa(CIS.train.df, 3)
fit3
fa.diagram(fit3)
```

# Run CFA on CIS with new model
```{r}
mod <- '
  decision =~ D1 + D2 + D3 + D4 + D5 + D6 + T3
  epistemic =~ E1 + E2 + E4 + E5 + T2

  decision ~~ epistemic
'

fit <- cfa(mod, CIS.df[-inds,])
summary(fit, standardized = TRUE, fit.measures = TRUE, modindices = TRUE)
semPaths(fit)#, what = 'diagram', whatLabels = 'stand', layout = 'tree2', residuals = FALSE, nCharNodes = 10, edge.color = 'black', edge.label.cex = 1.5, curve = 4, label.scale = FALSE, nodeLabels = c('D1', 'D2', 'D3', 'D4', 'D5', 'D6', 'E1', 'E2', 'E4', 'E5', 'Decision-making\nagency', 'Epistemic\nagency'), rotation = 2, sizeMan = 6, sizeLat = 24, width = 4, height = 5, mar = c(1, 6, 1, 2), fixedStyle = c(lty = 1), shapeLat = 'ellipse')
```

```{r}
df.matched <- df.matched %>%
  mutate(Lab.goal.skills = 1 * (Lab.goal == 'Skills-based'),
         Lab.goal.both = 1 * (Lab.goal == 'Mixed'),
         Lab.goal.concepts = 1 * (Lab.goal == 'Concepts-based'))

mod.sem <- '
  level: 1
    student.score.post ~ student.score.pre
  level: 2
    decision =~ 1.0 * Q35_1 + 1.310 * Q35_2 + 1.122 * Q35_3 + 1.013 * Q35_4 + 0.807 * Q35_5 + 0.906 * Q36_6
    #epistemic =~ 1.0 * Q36_1 + 0.990 * Q36_2 + 0.899 * Q36_4 + 0.593 * Q36_5

    #decision ~~ 0.241 * epistemic
    #Q36_1 ~~ 0.131 * Q36_2 + -0.004 * Q36_3
    #Q36_2 ~~ 0.165 * Q36_4
    #Q36_3 ~~ 0.344 * Q36_4
    Q35_1 ~~ 0.524 * Q35_1
    Q35_2 ~~ 0.297 * Q35_2
    Q35_3 ~~ 0.645 * Q35_3
    Q35_4 ~~ 0.570 * Q35_4
    Q35_5 ~~ 0.632 * Q35_5
    Q36_6 ~~ 0.630 * Q36_6
    #Q36_1 ~~ 0.379 * Q36_1
    #Q36_2 ~~ 0.272 * Q36_2
    #Q36_4 ~~ 0.532 * Q36_4
    #Q36_5 ~~ 0.561 * Q36_5
    decision ~~ 0.556 * decision
    #epistemic ~~ 0.534 * epistemic

    decision ~ Lab.goal.skills + Lab.goal.both
    #epistemic ~ Lab.goal.skills + Lab.goal.both

    student.score.post ~ decision + Lab.goal.skills + Lab.goal.both
'

fit <- sem(mod.sem, data = df.matched, cluster = "ResponseId.CIS")
summary(fit, standardized = TRUE, fit.measures = TRUE, modindices = TRUE)
standardizedsolution(fit)
resid(fit, type = 'cor')
```




