---
output:
  pdf_document: default
  html_document: default
---
# Load necessary packages
```{r, results = 'hide', message = FALSE, warning = FALSE}
library(tidyverse)
library(data.table)
library(reshape2)
library(ggpubr)
library(lmerTest)
library(sjstats)
library(sjPlot)
library(gridExtra)
library(stargazer)
library(lavaan)
library(semPlot)
library(psych)
theme_set(theme_classic(base_size = 14))
```

# Scoring/cleaning functions
```{r}
Read.Score <- function(file){
  dt <- fread(file)
  answers.cols <- names(dt)[grep('(a|b)$', names(dt))]
  
  dt[, (answers.cols) := lapply(.SD, function(x) case_when(x == 5 ~ 1,
                                                           x == 1 ~ -1,
                                                           TRUE ~ 0)),
     .SDcols = answers.cols]
  df <- dt[, -c('q40a', 'q40b')]

  df$student.score <- rowSums(df %>% select(grep("a$", names(.))))
  df$expert.score <- rowSums(df %>% select(grep("b$", names(.))))
  
  return(df)
}

Read.duplicate.cis <- function(file){
  cis.df <- read.csv(file)
  
  cis.noInfo <- cis.df[(cis.df$Q33 == '') | is.na(cis.df$Q33),]
  cis.FullInfo <- cis.df[(cis.df$Q33 != '') & !is.na(cis.df$Q33),]
  
  original.cols <- c('Q5', 'Q52',	'Q53', 'Q27', 'Q6',	'Q11', 'Q19',	'Q20', 'StartDate',
                     'anon_instructor_id', 'ResponseId', 'pre_survey_id', 'post_survey_id')

  cis.noInfo <- left_join(cis.noInfo, cis.FullInfo, 
                          by = c('anon_university_id', 'Q18'), 
                          suffix = c('.original', '.copy')) %>%
    select(anon_university_id, Q18, Q15.copy,	Q21.copy,	Q22_1.copy,	Q22_2.copy,	Q23.copy, 
           Q29.copy, grep('Q(3|4)\\d_?\\d?\\.copy', names(.)), 
           paste(original.cols, '.original', sep = '')) %>%
    filter(!duplicated(ResponseId.original) & !is.na(ResponseId.original)) %>%
    `colnames<-`(unlist(lapply(names(.), function (x) strsplit(x, '\\.')[[1]][1])))
  
  cis.df <- rbind(cis.FullInfo, cis.noInfo[, names(cis.df)])
  return(cis.df)
}
```

# Read, score, and match
```{r}
#cis.df <- Read.duplicate.cis('C:/Users/Cole/Documents/GRA_Summer2020/eclass-public-analysis/anon_cis.csv')

cis.df <- read.csv('C:/Users/Cole/Documents/GRA_Summer2020/eclass-public-analysis/anon_cis_CW.csv')

pre.df <- Read.Score('C:/Users/Cole/Documents/GRA_Summer2020/eclass-public-analysis/anon_pre.csv')

cis.pre.df <- right_join(cis.df, pre.df, by = c('pre_survey_id' = 'survey_id'))

post.df <- Read.Score('C:/Users/Cole/Documents/GRA_Summer2020/eclass-public-analysis/anon_post.csv')

full.df <- full_join(cis.pre.df, post.df, 
                     by = c('post_survey_id' = 'survey_id', 
                            'anon_student_id'), suffix = c('.pre', '.post'))

print('Total # of students in dataset...')
nrow(full.df)

print('Total # of classes in dataset...')
length(unique(full.df$ResponseId))

# Remove whole classes without goal and/or level information
full.df <- full.df %>%
  filter(Q33 != '')

print('# of remaining students in full dataset...')
nrow(full.df)

print('# of remaining classes in full dataset...')
length(unique(full.df$ResponseId))

df.matched <- full.df %>%
  filter(!is.na(student.score.pre) & !is.na(student.score.post))

print('# of students in matched dataset...')
nrow(df.matched)

print('# of classes in matched dataset...')
length(unique(df.matched$ResponseId))
```

# Data processing
```{r}
# Replace declared major with intended major in cases where students intend to switch
df.matched[is.na(df.matched$Q48) | (df.matched$Q48 == 0),
'Q48'] <- df.matched[is.na(df.matched$Q48) | (df.matched$Q48 == 0), 'Q47']

df.matched <- df.matched %>%
  mutate(Major = case_when(
    Q48 == 1 ~ 'Physics',
    Q48 == 2 ~ 'Chemistry',
    Q48 == 3 ~ 'Biochemistry',
    Q48 == 4 ~ 'Biology',
    Q48 == 5 ~ 'Engineering',
    Q48 == 6 ~ 'Engineering Physics',
    Q48 == 7 ~ 'Astronomy',
    Q48 == 8 ~ 'Astrophysics',
    Q48 == 9 ~ 'Geology/geophysics',
    Q48 == 10 ~ 'Math/applied math',
    Q48 == 11 ~ 'Computer science',
    Q48 == 12 ~ 'Physiology',
    Q48 == 13 ~ 'Other science',
    Q48 == 14 ~ 'Non-science',
    Q48 == 15 ~ 'Open/undeclared',
    TRUE ~ 'Unknown'
  ),
  Gender = case_when(
    Q54 == 1 ~ 'Woman',
    Q54 == 2 ~ 'Man',
    Q54 == 3 ~ 'Other',
    TRUE ~ 'Unknown'
  ),
  Lab.goal = case_when(
    Q33 == 'Reinforce physics concepts.' ~ 'Concepts',
    Q33 == 'Both about equally.' ~ 'Both',
    Q33 == 'Develop lab skills.' ~ 'Skills',
    TRUE ~ NA_character_
  ),
  Lab.level = case_when(
    Q18 == 'Beyond the first year lab' ~ 'BFY',
    Q27 == 'Calculus-based' ~ 'FY.Calc',
    Q27 == 'Algebra-based' ~ 'FY.Alg',
    TRUE ~ NA_character_
  )) %>%
  mutate(Major = case_when(
    (Major == 'Physics') | (Major == 'Engineering Physics') | (Major == 'Astronomy') | 
      (Major == 'Astrophysics') ~ 'Physics',
    (Major == 'Chemistry') | (Major == 'Biochemistry') | (Major == 'Biology') | 
      (Major == 'Physiology') ~ 'Chem.LifeSci',
    Major == 'Engineering' ~ 'Engineering',
    (Major == 'Math/applied math') | (Major == 'Computer science') ~ 'Math.CS',
    (Major == 'Geology/geophysics') | (Major == 'Other science') ~ 'OtherSci',
    Major == 'Non-science' ~ 'NonSci',
    Major == 'Open/undeclared' ~ 'Undeclared',
    Major == 'Unknown' ~ 'Unknown',
    TRUE ~ NA_character_
  )) %>%
  mutate(Major = relevel(as.factor(Major), ref = 'Physics'),
         Gender = relevel(as.factor(Gender), ref = 'Man'),
         Lab.goal = relevel(as.factor(Lab.goal), ref = 'Concepts'),
         Lab.level = relevel(as.factor(Lab.level), ref = 'FY.Alg'))

df.matched$Race.ethnicity.Native = relevel(factor(ifelse((df.matched$Q52_5 == 1) | 
                                                      (df.matched$Q52_1 == 1), 1, 0),
                                                  levels = c(1, 0)), ref = '0')
new.race.cols <- c('Race.ethnicity.Other', 'Race.ethnicity.Black', 
                 'Race.ethnicity.Hispanic', 'Race.ethnicity.Asian', 
                 'Race.ethnicity.White', 'Race.ethnicity.Unknown')
setnames(df.matched, old = c('Q52_7', 'Q52_3', 'Q52_4', 'Q52_2', 'Q52_6', 
                             'race_unknown'), new = new.race.cols)
df.matched[is.na(df.matched)] <- 0
df.matched[new.race.cols] <- lapply(df.matched[new.race.cols], factor, levels = c(1, 0))
df.matched[new.race.cols] <- lapply(df.matched[new.race.cols], relevel, ref = '0')
```

# Descriptive statistics
```{r}
plot.pre.post <- function(df, var){
  if(var == 'Race.ethnicity'){
    print(colSums(sapply(df[, c('Race.ethnicity.Native', new.race.cols)], 
                         function (x) as.numeric(as.character(x)))))
    
    df.long <- reshape2::melt(df.matched, id.vars = c('Race.ethnicity.Native', 
                                                      new.race.cols), 
                              measure.vars = c('student.score.pre', 'student.score.post'),
                              variable.name = 'Time', value.name = 'Score') %>%
      reshape2::melt(., measure.vars = c('Race.ethnicity.Native', new.race.cols), 
                     id.vars = c('Time', 'Score'), variable.name = 'Race.ethnicity') %>%
      filter(value == 1) %>%
      select(Time, Score, Race.ethnicity) %>%
      rowwise() %>%
      mutate(Race.ethnicity = strsplit(as.character(Race.ethnicity), '\\.')[[1]][3])
    
  } else {
    print(table(df[, var]))
    df.long <- reshape2::melt(df, measure.vars = c('student.score.pre',
                                                   'student.score.post'), 
                              variable.name = 'Time', value.name = 'Score')
  }
  
  p <- ggplot(df.long, aes_string(x = var, y = 'Score', group = 'Time', color = 'Time'))
  add_summary(p, fun = 'mean_se', group = c('Time')) +
    scale_color_manual(labels = c('pre', 'post'), values = c('#2271B2', '#D55E00')) +
    theme(axis.text.x = element_text(angle = 90))
}

plot.pre.post(df.matched, 'Major')
plot.pre.post(df.matched, 'Gender')
plot.pre.post(df.matched, 'Race.ethnicity')
plot.pre.post(df.matched, 'Lab.goal')
```

# Mixed-effects models
```{r}
mod1 <- lmer(student.score.post ~ student.score.pre + Lab.goal + Lab.level + Major + 
               Gender + Race.ethnicity.Native + Race.ethnicity.Other +
               Race.ethnicity.Black + Race.ethnicity.Hispanic + Race.ethnicity.Asian + 
               Race.ethnicity.White + Race.ethnicity.Unknown + (1 | ResponseId), 
             df.matched)
summary(mod1)

mod2 <- lmer(student.score.post ~ student.score.pre + Lab.level + Lab.goal * 
               (Gender + Race.ethnicity.Native + Race.ethnicity.Other + 
                  Race.ethnicity.Black + Race.ethnicity.Hispanic + Race.ethnicity.Asian + 
                  Race.ethnicity.White + Race.ethnicity.Unknown) + Major + 
               (1 | ResponseId), df.matched)
summary(mod2)

r2(mod1)
r2(mod2)
```

# Marginal effects plots
```{r}
# Main effect of lab goal from Model 1
p1 <- plot_model(mod1, type = 'eff', terms = 'Lab.goal', dot.size = 4, line.size = 1, 
                 ci.lvl = 0.67, title = '', 
                 axis.title = 'Predicted E-CLASS posttest scores', 
                 colors = c('#e69f00', '#009e74', '#0071b2'), dodge = 0.5) +
  theme(legend.position = 'right') +
  scale_x_discrete(limits = c("Reinforce concepts", "Both about equally", 
                              "Develop skills"))

p1.new <- p1
p1.new$data$x <- c(1, 2, 3)
p1.new

# Effects of gender across lab goal from Model 2

p2 <- plot_model(mod2, type = 'eff', terms = c('Gender', 'Lab.goal'), dot.size = 4, 
                 line.size = 1, ci.lvl = 0.67, title = '', 
                 axis.title = 'Predicted E-CLASS posttest scores', 
                 colors = c('#e69f00', '#009e74', '#0071b2'), dodge = 0.5) +
  theme(legend.position = 'right')

p2.new <- p2
p2.new$data$group <- factor(p2.new$data$group, levels = c("Concepts", "Both", "Skills"))
p2.new
```

# Race/ethnicity marginal effects plots
```{r}
p3.native <- plot_model(mod2, type = 'eff', terms = c('Race.ethnicity.Native [1]', 
                                                      'Lab.goal'))
df.race.eff <- data.frame(p3.native$data) %>%
  mutate(race.ethnicity = 'Race.ethnicity.Native')
for(race in c(new.race.cols)){
  p3 <- plot_model(mod2, type = 'eff', terms = c(paste(race, ' [1]', sep = ''),
                                                 'Lab.goal'))
  df.race.eff <- rbind(df.race.eff, data.frame(p3$data) %>%
                         mutate(race.ethnicity = race))
}

df.race.eff <- df.race.eff %>%
  mutate(group = factor(group, levels = c('Concepts', 'Both', 'Skills'), 
                        ordered = TRUE)) %>%
  rowwise() %>%
  mutate(race.ethnicity = strsplit(race.ethnicity, '\\.')[[1]][3])

ggplot(df.race.eff, aes(x = race.ethnicity, y = predicted, group = group, color = group)) +
  geom_point(size = 4, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), size = 1, width = 0.2,
                position = position_dodge(width = 0.5)) +
  scale_color_manual(values = c('#e69f00', '#009e74', '#0071b2')) +
  labs(x = 'Race/ethnicity', y = 'Predicted E-CLASS posttest scores', color = 'Lab goal')
```

# Build measurement model for latent class variables
```{r}
df.matched[, names(df.matched) %like% "Q35|Q36"] <- data.frame(lapply(df.matched[, names(df.matched) %like% "Q35|Q36"], function(x) factor(as.vector(x), levels = c('Never', 'Rarely', 'Sometimes', 'Often', 'Always'), ordered = TRUE)))

mod <- '
  agency =~ Q35_1 + Q35_2 + Q35_3 + Q35_4 + Q35_5 + Q36_6
  modeling =~ Q36_1 + Q36_2 + Q36_3 + Q36_4 + Q36_5
'

fit <- sem(mod, unique(df.matched[, names(df.matched) %like% "Q35|Q36"]))
summary(fit, standardized = TRUE, fit.measures = TRUE, modindices = TRUE)
semPaths(fit, whatLabels = 'std', edge.color = 'black', curve = 2, residuals = FALSE, label.scale = TRUE, mar = c(8, 8, 8, 8))
```

# With numeric data
```{r}
df.matched[, names(df.matched) %like% "Q35|Q36"] <- data.frame(lapply(df.matched[, names(df.matched) %like% "Q35|Q36"], function(x) as.numeric(x)))

fit <- sem(mod, unique(df.matched[, names(df.matched) %like% "Q35|Q36"]))
summary(fit, standardized = TRUE, fit.measures = TRUE, modindices = TRUE)
semPaths(fit, whatLabels = 'std', edge.color = 'black', curve = 2, residuals = FALSE, label.scale = TRUE, mar = c(8, 8, 8, 8))
```

# EFA
```{r}
fa.parallel(unique(df.matched[, names(df.matched) %like% "Q35|Q36"]))
fit <- fa(unique(df.matched[, names(df.matched) %like% "Q35|Q36"]), 2)
fit
fa.diagram(fit)
```

# CFA with model suggested by EFA (only minor changes that I think are theoretically justifiable)
```{r}
mod <- '
  agency =~ Q35_1 + Q35_2 + Q35_3 + Q35_4 + Q36_6 + Q35_5
  modeling =~ Q36_1 + Q36_2 + Q36_4
'

fit <- sem(mod, unique(df.matched[, names(df.matched) %like% "Q35|Q36"]))
summary(fit, standardized = TRUE, fit.measures = TRUE, modindices = TRUE)
semPaths(fit, whatLabels = 'std', edge.color = 'black', curve = 2, residuals = FALSE, label.scale = TRUE, mar = c(8, 8, 8, 8))
```
*This seems like a good model to move forward with. We drop two items from the modeling factor. For the record, I'm okay with adding them back in, but they will increase our variance maybe more than we can afford.*

# Larger SEM model with latent class variables as mediating variables in the analysis
```{r}
df.matched <- df.matched %>%
  mutate(Lab.goal.skills = 1 * (Lab.goal == 'Skills'),
         Lab.goal.both = 1 * (Lab.goal == 'Both'),
         Lab.goal.concepts = 1 * (Lab.goal == 'Concepts'))

mod.sem <- '
  level: 1
    student.score.post ~ student.score.pre
  level: 2
    agency =~ Q35_1 + Q35_2 + Q35_3 + Q35_4 + Q36_6 + Q35_5
    modeling =~ Q36_1 + Q36_2 + Q36_4

    agency ~ Lab.goal.skills + Lab.goal.both
    modeling ~ Lab.goal.skills + Lab.goal.both

    student.score.post ~ agency + modeling + Lab.goal.skills + Lab.goal.both
'

fit <- sem(mod.sem, data = df.matched, cluster = "ResponseId")
summary(fit, standardized = TRUE, fit.measures = TRUE, modindices = TRUE)
```

