---
output:
  html_document: default
  pdf_document: default
---
# Setup
```{r global_options, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

## Load necessary packages
```{r, results = 'hide'}
library(easypackages)
libraries('plyr', 'tidyverse', 'data.table', 'reshape2', 'ggpubr', 'lmerTest', 
          'reghelper', 'car', 'lattice', 'sjstats', 'sjPlot', 'gridExtra', 
          'stargazer', 'lavaan', 'semPlot', 'psych', 'grid', 'effectsize', 
          'mice', 'miceadds', 'broom.mixed', 'ggeffects', 'plotly')
source('C:/Users/Cole/Documents/GitHub/PLIC/Processing-Scripts/PLIC_DataProcessing.R')
source('ECLASS_Processing.R')
```

## Read, score, and match

### PLIC
```{r}
df.PLIC.full <- read.csv('C:/Users/Cole/Documents/DATA/PLIC_DATA/Collective_Surveys/Complete/Complete_Concat_CourseInfo.csv') %>%
  filter(Survey_x == 'C' | Survey_y == 'C') %>% # remove events with no CR surveys
  mutate(V4_x = as.Date(V4_x),
         V4_y = as.Date(V4_y)) %>%
  filter(V4_y < as.Date('2021-01-01') | (is.na(V4_y) &
                                           V4_x < as.Date('2021-01-01'))) %>%
  filter((Lab_level == 'Intro-Algebra') | (Lab_level == 'Intro-Calculus'))

# Remove FR scores
df.PLIC.full[(df.PLIC.full$Survey_x == 'F'), 'PreScores'] <- NA_real_
df.PLIC.full[(df.PLIC.full$Survey_y == 'F'), 'PostScores'] <- NA_real_
df.PLIC.full <- df.PLIC.full %>%
  filter(!is.na(PreScores) | !is.na(PostScores))

# Remove whole classes without goal and/or level information or that were only administered at pre or post
df.PLIC.course <- data.table(df.PLIC.full)[, 
                                           `:=`(N.students = .N, 
                                                pre.rate = sum(Survey_x == 'C')/.N,
                                                post.rate = sum(Survey_y == 'C')/.N), 
                                           .(Class_ID)] %>%
  data.frame(.)

df.PLIC.course <- df.PLIC.course %>%
  filter(!is.na(Lab_purpose) & (Lab_purpose != '') & (pre.rate > 0) & 
           (post.rate > 0))

df.PLIC.course <- df.PLIC.course %>%
  Collapse.vars(.) %>%
  mutate(Lab.type = relevel(as.factor(case_when(
    Lab_purpose == 'Reinforce concepts' ~ 'Concepts-based',
    Lab_purpose == 'Both about equally' ~ 'Mixed',
    Lab_purpose == 'Develop lab skills' ~ 'Skills-based')), 
    ref = 'Concepts-based'))

df.PLIC.course <- df.PLIC.course[, names(df.PLIC.course)[names(df.PLIC.course) %like% 'Race|Gender|Major|Lab.type|Scores|Class_ID|Institution_type|institution_id|student_id$|Q28|Q29|Q31|Q32|Q33']] %>%
  mutate(Assessment = 'PLIC',
         anon_institution_id = 1000 + anon_institution_id)
# differentiate E-CLASS and PLIC institutions

# get matched dataset
df.PLIC.matched <- df.PLIC.course %>%
  filter(!is.na(PreScores) & !is.na(PostScores))
```

### E-CLASS
```{r}
# read course information survey (CIS) and pre/post survey data
df.cis <- read.csv('C:/Users/Cole/Documents/GRA_Summer2020/eclass-public-analysis/anon_cis_CW.csv')
names(df.cis) <- paste(names(df.cis), '.CIS', sep = '')
df.pre <- Read.Score('C:/Users/Cole/Documents/GRA_Summer2020/eclass-public-analysis/anon_pre.csv')
names(df.pre) <- paste(names(df.pre), '.pre', sep = '')
df.pre$pre.id <- row.names(df.pre)

# join CIS on presurvey
df.cis.pre <- right_join(df.cis, df.pre, 
                         by = c('pre_survey_id.CIS' = 'survey_id.pre'))
df.post <- Read.Score('C:/Users/Cole/Documents/GRA_Summer2020/eclass-public-analysis/anon_post.csv')
names(df.post) <- paste(names(df.post), '.post', sep = '')
df.post$post.id <- row.names(df.post)

df.cis.post <- right_join(df.cis, df.post,
                          by = c('post_survey_id.CIS' = 'survey_id.post'))
matched.df <- inner_join(df.cis.pre, df.cis.post, 
                         by = c(names(df.cis), 
                                'anon_student_id.pre' = 'anon_student_id.post'))

df.ECLASS.full <- rbind.fill(matched.df, df.cis.pre[!(df.cis.pre$pre.id %in% 
                                                        matched.df$pre.id),],
                             df.cis.post[!(df.cis.post$post.id %in%
                                             matched.df$post.id),])

df.ECLASS.full <- df.ECLASS.full %>%
  Collapse.vars.ECLASS(.) %>%
  mutate(anon_student_id = ifelse(!is.na(anon_student_id.post),
                                  anon_student_id.post, 
                                  anon_student_id.pre)) %>%
  filter(Course.level == 'FY') # only examining FY courses

df.ECLASS.full <- 
  data.table(df.ECLASS.full)[, 
                             `:=`(N.students = .N, 
                                  pre.rate = sum(!is.na(student.score.pre))/.N,
                                  post.rate = sum(!is.na(student.score.post))/.N), 
                             .(ResponseId.CIS)] %>%
  data.frame() %>%
  rename.vars(., df.PLIC.course) %>%
  recode.CIS(.)

# remove whole classes without type and/or level information
df.ECLASS.course <- df.ECLASS.full %>%
  filter(!is.na(Lab.type) & !is.na(Course.level) & (pre.rate > 0) & 
           (post.rate > 0))

df.ECLASS.course <- df.ECLASS.course[, names(df.ECLASS.course)[names(df.ECLASS.course) %like% 'Race|Gender|Major|Lab.type|Scores|Class_ID|Institution_type|institution_id|student_id$|Q28_|Q29_|Q31_|Q32_|Q33_']] %>%
  mutate(Assessment = 'E-CLASS')

# get matched dataset
df.ECLASS.matched <- df.ECLASS.course %>%
  filter(!is.na(PreScores) & !is.na(PostScores))

# combined E-CLASS and PLIC datasets
df.course <- rbind(df.PLIC.course, df.ECLASS.course)
df.matched <- rbind(df.PLIC.matched, df.ECLASS.matched)

rm(df.cis, df.cis.pre, df.cis.post, df.pre, df.post)
```

# Summary of datasets
```{r}
summary.datasets <- function(df.full, df.course, df.matched){
  df <- data.frame(N.student.records = unlist(lapply(list(df.full, df.course,
                                                          df.matched), 
                                                     function(x) nrow(x))),
                   N.students = unlist(lapply(list(df.full, df.course, df.matched),
                                              function(x) 
                                                length(unique(x[, 'anon_student_id'])))),
                   N.classes = unlist(lapply(list(df.full, df.course, df.matched), 
                                             function(x) 
                                               length(unique(x[, 'Class_ID'])))),
                   N.institutions = unlist(lapply(list(df.full, df.course,
                                                       df.matched), function(x)
                                                         length(unique(x[, 'anon_institution_id'])))),
                   dataset = c('full dataset', 'course info', 'matched'))
  
  return(df)
}

rbind(summary.datasets(df.ECLASS.full, df.ECLASS.course, df.ECLASS.matched) %>%
        mutate(Assessment = 'E-CLASS'), 
      summary.datasets(df.PLIC.full, df.PLIC.course, df.PLIC.matched) %>%
        mutate(Assessment = 'PLIC'))

# Breakdown of institution type and lab type
table(df.matched[!duplicated(df.matched$anon_institution_id), 
                 c('Institution_type', 'Assessment')], exclude = NULL)
table(df.matched[!duplicated(df.matched$Class_ID), 
                 c('Lab.type', 'Assessment')], exclude = NULL)

rm(df.ECLASS.full, df.PLIC.full)
```

# Analysis

## Students' scores by demographics and type of lab

### Demographic breakdowns
```{r}
Race.ethnicity.cols <- names(df.matched)[names(df.matched) %like% 'Race']
Race.ethnicity.table <- function(df, col, Lab.type = FALSE){
  # race/ethnicity variables are not independent...this function calculates tables
  # for each of those variables
  if(Lab.type){
      tab <- table(df[, c(col, 'Lab.type', 'Assessment')], exclude = NULL)
  } else {
    tab <- table(df[, c(col, 'Assessment')], exclude = NULL)
  }
  return(data.frame(tab) %>%
           filter(get(col) == 1))
}

# get demographic breakdowns across lab type
table(df.matched[, c('Lab.type', 'Assessment')], exclude = NULL)
table(df.matched[, c('Gender', 'Assessment')], exclude = NULL)

rbind.fill(lapply(Race.ethnicity.cols, Race.ethnicity.table, df = df.matched)) %>%
  melt(id.vars = c('Assessment', 'Freq')) %>%
  filter(value == 1) %>%
  select(Assessment, variable, Freq) %>%
  arrange(Assessment, variable)

table(df.matched[, c('Gender', 'Lab.type', 'Assessment')], exclude = NULL)

rbind.fill(lapply(Race.ethnicity.cols, Race.ethnicity.table, df = df.matched, 
                  Lab.type = TRUE)) %>%
  melt(id.vars = c('Assessment', 'Lab.type', 'Freq')) %>%
  filter(value == 1) %>%
  select(Assessment, Lab.type, variable, Freq) %>%
  arrange(Assessment, variable)
```

### Mixed-effects models

Fit null model with random intercepts for class and institution, which measures the interclass correlation coefficient (ICC; the amount of variance explained by the random effects in our model alone). Then, we fit our model of interest.
```{r}
formula.null <- as.formula('PostScores ~ (1 | anon_institution_id/Class_ID)')
formula.main <- as.formula('PostScores ~ PreScores + Lab.type * (Gender + 
                            Race.ethnicity.AmInd + Race.ethnicity.NatHawaii + 
                            Race.ethnicity.Other + Race.ethnicity.Black +
                            Race.ethnicity.Hispanic + Race.ethnicity.Asian + 
                            Race.ethnicity.White) + 
                            Major + (1 | anon_institution_id/Class_ID)')

print(paste('E-CLASS null R2:', 
            as.numeric(r2(lmer(formula.null, df.ECLASS.matched))$R2_conditional)))
print(paste('PLIC null R2:', 
            as.numeric(r2(lmer(formula.null, df.PLIC.matched))$R2_conditional)))


mod.ECLASS <- lmer(update(formula.main, ~. + Lab.type * Race.ethnicity.unknown),
                   df.ECLASS.matched)
mod.PLIC <- lmer(formula.main, df.PLIC.matched)

print(paste('E-CLASS conditional R2:', 
            as.numeric(r2(mod.ECLASS)$R2_conditional)))
print(paste('PLIC conditional R2:', 
            as.numeric(r2(mod.PLIC)$R2_conditional)))

print(paste('E-CLASS marginal R2:', 
            as.numeric(r2(mod.ECLASS)$R2_marginal)))
print(paste('PLIC marginal R2:', 
            as.numeric(r2(mod.PLIC)$R2_marginal)))

mod.ECLASS.std <- standardize_parameters(mod.ECLASS, ci = 0.67)
mod.ECLASS.std$uncertainty <- abs(mod.ECLASS.std$Std_Coefficient - 
                                    mod.ECLASS.std$CI_low)

mod.PLIC.std <- standardize_parameters(mod.PLIC, ci = 0.67)
mod.PLIC.std$uncertainty <- abs(mod.PLIC.std$Std_Coefficient - 
                                    mod.PLIC.std$CI_low)
```

#### Output stargazer
```{r, include = FALSE}
labels = c("Pretest", "Mixed", "Skills-based", "Non-binary", "Unknown", "Woman",
            "American Indian", "Native Hawaiian", "Other", "Black", "Hispanic",
            "Asian", "White", "LifeSci/Chem", "Engineering", "Math/CS",
            "Non-science", "Other", "Other science", "Undeclared", "Unknown",
            "Unknown race", "Mixed * Non-binary", "Skills-based * Non-binary",
            "Mixed * Unknown", "Skills-based * Unknown", "Mixed * Woman",
            "Skills-based * Woman", "Mixed * American Indian",
            "Skills-based * American Indian", "Mixed * Native Hawaiian",
            "Skills-based * Native Hawaiian", "Mixed * Other",
            "Skills-based * Other", "Mixed * Black", "Skills-based * Black",
            "Mixed * Hispanic", "Skills-based * Hispanic", "Mixed * Asian",
            "Skills-based * Asian", "Mixed * White", "Skills-based * White",
            "Mixed * Unknown race", "Skills-based * Unknown race", "Constant")

ECLASS.std.coefs <- mod.ECLASS.std$Std_Coefficient
ECLASS.std.delta <- mod.ECLASS.std$uncertainty
names(ECLASS.std.coefs) <- names(summary(mod.ECLASS)$coefficients[, 1])
names(ECLASS.std.delta) <- names(summary(mod.ECLASS)$coefficients[, 2])

PLIC.std.coefs <- mod.PLIC.std$Std_Coefficient
PLIC.std.delta <- mod.PLIC.std$uncertainty
names(PLIC.std.coefs) <- names(summary(mod.PLIC)$coefficients[, 1])
names(PLIC.std.delta) <- names(summary(mod.PLIC)$coefficients[, 2])

class(mod.ECLASS) <- "lmerMod"
class(mod.PLIC) <- "lmerMod"

out <- stargazer(mod.ECLASS, mod.ECLASS, mod.ECLASS, mod.ECLASS, mod.PLIC, 
                 mod.PLIC, mod.PLIC, mod.PLIC, 
                 coef = list(summary(mod.ECLASS)$coefficients[, 1],
                             summary(mod.ECLASS)$coefficients[, 2], 
                             ECLASS.std.coefs, ECLASS.std.delta,
                             summary(mod.PLIC)$coefficients[, 1],
                             summary(mod.PLIC)$coefficients[, 2], 
                             PLIC.std.coefs, PLIC.std.delta),
                 se = list(summary(mod.ECLASS)$coefficients[, 2], NA, 
                           ECLASS.std.delta, NA, 
                           summary(mod.PLIC)$coefficients[, 2], NA, 
                           PLIC.std.delta, NA), type = 'latex', 
                 intercept.bottom = TRUE, style = 'asr', 
                 column.labels = c('Beta', 'SE', 'Beta.std', 'SE', 'Beta', 'SE', 
                                   'Beta.std', 'SE'), model.numbers = FALSE,
                 covariate.labels = labels, 
                 dep.var.labels = 'E-CLASS posttest scores',
                 out = 'LabType_Model.tex')
```

#### Marginal effects plots
```{r}
theme_set(theme_classic(base_size = 14)) # set font size for ggplot
get_legend <- function(myggplot){
  # from http://www.sthda.com/english/wiki/wiki.php?id_contents=7930
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}

marginal.plots <- function(mod, assessment, y.low, y.high, keep.legend = FALSE, 
                           labs = TRUE){
  theme.margEff <- theme(axis.text.x = element_text(angle = 40, vjust = 1, 
                                                    hjust = 1), 
                         axis.ticks.y = element_blank(),
                         axis.text.y = element_blank())
  margins <- unit(c(0, 0, 0, 0), 'cm')
  
  # marginal effects (average effect) of different labs on posttest scores
  pred.labs <- data.frame(ggeffect(mod, "Lab.type", ci.lvl = 0.67))
  
  p1 <- ggplot(pred.labs, aes(x = factor(x), y = predicted, color = factor(x))) +
    geom_point(size = 2) +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high), size = 1, width = 0,
                  position = position_dodge(width = 0.5)) +
    scale_x_discrete(labels = c('Concepts-based', 'Mixed', 'Skills-based')) +
    scale_color_manual(values = c('#e69f00', '#009e74', '#0071b2')) +
    ylab(paste('Expected ', assessment, '\nposttest scores', sep = '')) +
    theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust = 1),
          legend.position = 'none',
          plot.margin = margins) +
    ylim(y.low, y.high)
  
  # average over lab type and gender
  pred.labs.gender <- data.frame(ggeffect(mod, c("Gender", "Lab.type"), 
                                          ci.lvl = 0.67))
  
  p2 <- ggplot(pred.labs.gender, aes(x = factor(x), y = predicted, 
                                     color = group)) +
    geom_point(size = 2, position = position_dodge(width = 0.5)) +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high), size = 1, width = 0,
                  position = position_dodge(width = 0.5)) +
    scale_color_manual(values = c('#e69f00', '#009e74', '#0071b2')) +
    scale_x_discrete(limits = c("Man", "Non-binary", "Woman", "Unknown")) +
    labs(y = '', color = 'Lab type') +
    theme.margEff +
    theme(plot.margin = margins)
    ylim(y.low, y.high)
  
  if(keep.legend){
    p2 <- p2 +
      theme(legend.position = 'top')
    
    leg <- get_legend(p2)
  }
  p2 <- p2 +
    theme(legend.position = 'none')
  
  # average over lab type and race/ethnicity...since race/ethnicity variables are
  # not independent, we calculate marginal effects separately for each variable...
  race.cols <- 
    names(summary(mod)$coefficients[, 1])[names(summary(mod)$coefficients[, 1])
                                          %like% '^Race']
  preds.labs.race <- data.frame(ggeffect(mod, c(race.cols[1], "Lab.type"), 
                                         ci.lvl = 0.67))
  
  
  preds.labs.race <- preds.labs.race %>%
    filter(x == 1) %>%
    mutate(x = race.cols[1])
  for(race in c(race.cols[2:length(race.cols)])){
    temp.data <- data.frame(ggeffect(mod, c(race, 'Lab.type'), ci.lvl = 0.67))
    # ...bind results in one dataframe...
    preds.labs.race <- rbind(preds.labs.race, temp.data %>% 
                               filter(x == 1) %>%
                               mutate(x = race))
  }
  
  # ...and clean up the dataframe a little bit
  preds.labs.race$race.ethnicity <-
    sapply(strsplit(as.character(preds.labs.race$x), "\\."), "[[", 3)
  
  preds.labs.race <- preds.labs.race %>%
    mutate(group = factor(group, levels = c('Concepts-based', 'Mixed', 
                                            'Skills-based'),
                          ordered = TRUE),
           race.ethnicity = case_when(
             race.ethnicity == 'AmInd' ~ 'American Indian',
             race.ethnicity == 'NatHawaii' ~ 'Native Hawaiian',
             race.ethnicity == 'unknown' ~ 'Unknown',
             TRUE ~ race.ethnicity))
  
  p3 <- ggplot(preds.labs.race, aes(x = factor(race.ethnicity, 
                                               levels = c('American Indian', 
                                                          'Asian', 'Black', 
                                                          'Hispanic', 
                                                          'Native Hawaiian', 
                                                          'White', 'Other', 
                                                          'Unknown')), 
                                    y = predicted, group = group, color = group)) +
    geom_point(size = 2, position = position_dodge(width = 0.5)) +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high), size = 1, width = 0.2,
                  position = position_dodge(width = 0.5)) +
    scale_color_manual(values = c('#e69f00', '#009e74', '#0071b2')) +
    ylab('') +
    theme.margEff +
    theme(legend.position = 'none',
          plot.margin = margins) +
    ylim(y.low, y.high)
  
  if(labs){
    p1 <- p1 +
      xlab('Lab type')
    p2 <- p2 +
      xlab('Gender')
    p3 <- p3 +
      xlab('Race/ethnicity') 
  } else {
    p1 <- p1 +
      xlab('')
    p2 <- p2 +
      xlab('')
    p3 <- p3 +
      xlab('')
  }
  
  if(keep.legend){
    return(list(p1, p2, p3, leg))
  }
  return(list(p1, p2, p3))
}
```

##### Combined figure
```{r}
plots.ECLASS <- marginal.plots(mod.ECLASS, 'E-CLASS', 11.5, 19, 
                               keep.legend = TRUE, labs = FALSE)
plots.PLIC <- marginal.plots(mod.PLIC, 'PLIC', 4.25, 6.25, keep.legend = FALSE)

pdf('Figures/Labtype_Demos.pdf', width = 7, height = 7, onefile = FALSE)
grobs.ECLASS = cbind(ggplotGrob(plots.ECLASS[1][[1]]),
                     ggplotGrob(plots.ECLASS[2][[1]]),
                     ggplotGrob(plots.ECLASS[3][[1]]), size = "first")
grobs.PLIC = cbind(ggplotGrob(plots.PLIC[1][[1]]), ggplotGrob(plots.PLIC[2][[1]]),
                     ggplotGrob(plots.PLIC[3][[1]]), size = "first")
grid.arrange(plots.ECLASS[4][[1]], arrangeGrob(grobs.ECLASS),
             arrangeGrob(grobs.PLIC), heights = c(1, 10, 10))
dev.off()
```

##### Expected differences in marginal effects
```{r}
std.diff.margEff <- function(v1, v2, se1, se2){
  diff <- (v2 - v1)
  se <- sqrt((se1 ^ 2) + (se2 ^ 2))
  return(list(diff, se))
}

margEff.diff.labType <- function(mod, norm.factor){
  df <- data.frame(ggeffect(mod, "Lab.type", ci.lvl = 0.67))
  
  pred.concepts <- df[df$x == 'Concepts-based', 'predicted']/norm.factor
  se.concepts <- df[df$x == 'Concepts-based', 'std.error']/norm.factor
  
  pred.skills <- df[df$x == 'Skills-based', 'predicted']/norm.factor
  se.skills <- df[df$x == 'Skills-based', 'std.error']/norm.factor
  
  preds.diff <- std.diff.margEff(pred.concepts, pred.skills, se.concepts, 
                                 se.skills)
  return(preds.diff)
}

diffs.ECLASS <- margEff.diff.labType(mod.ECLASS, 
                                     sd(df.ECLASS.matched[, 'PostScores']))
diffs.PLIC <- margEff.diff.labType(mod.PLIC, sd(df.PLIC.matched[, 'PostScores']))

print(paste('Difference in standardized marginal effects of lab type (E-CLASS): ',
            diffs.ECLASS[[1]], ' +- ', diffs.ECLASS[[2]], sep = ''))
print(paste('Difference in standardized marginal effects of lab type (PLIC): ',
            diffs.PLIC[[1]], ' +- ', diffs.PLIC[[2]], sep = ''))
```

#### Variance inflation factors and model diagnostics
```{r}
vif(mod.ECLASS)
plot(mod.ECLASS, xlab = 'Fitted values', ylab = 'Residuals')
qqmath(mod.ECLASS)

vif(mod.PLIC)
plot(mod.PLIC, xlab = 'Fitted values', ylab = 'Residuals')
qqmath(mod.PLIC)
```

## Effect of pedagogical variables

### Get unique courses
```{r}
df.CIS <- 
  df.matched[!duplicated(df.matched[, names(df.matched)[names(df.matched) 
                                                        %like% "Q28|Q29|Q31|Q32|Q33|institution_id"]]),]
```

### CFA

#### Number 1
```{r}
mod.cfa <- '
  agency =~ Q29_1 + Q29_2 + Q29_3 + Q29_4 + Q29_5 + Q31_6
  modeling =~ Q31_1 + Q31_2 + Q31_3 + Q31_4 + Q31_5
  communication =~ Q33_1 + Q33_2 + Q33_3 + Q33_4
'

fit.cfa <- sem(mod.cfa, data = df.CIS)
summary(fit.cfa, standardized = TRUE, fit.measures = TRUE, modindices = TRUE)
standardizedsolution(fit.cfa)
colSums(1 * (abs(resid(fit.cfa, type = 'cor')$cov) > 0.2))
resid(fit.cfa, type = 'cor')$cov
```

#### Number 2
```{r}
mod.cfa <- '
  agency =~ Q29_2 + Q29_3 + Q29_4 + Q29_5 + Q31_6
  modeling =~ Q31_1 + Q31_2 + Q31_3 + Q31_4 + Q31_5
  communication =~ Q33_1 + Q33_2 + Q33_3
  
  Q31_1 ~~ Q31_2 + Q31_3
  Q31_4 ~~ Q31_3 + Q31_2
'

fit.cfa <- sem(mod.cfa, data = df.CIS)
summary(fit.cfa, standardized = TRUE, fit.measures = TRUE, modindices = TRUE)
standardizedsolution(fit.cfa, type = 'std.lv')
colSums(1 * (abs(resid(fit.cfa, type = 'cor')$cov) > 0.15))
resid(fit.cfa, type = 'cor')$cov
```

### Differences in pedagogical variables across different labs
```{r}
factorScores <- lavPredict(fit.cfa, df.CIS, method = 'regression')
df.CIS.scored <- cbind(na.omit(df.CIS), factorScores) %>%
  mutate(agency = agency/sd(agency),
         modeling = modeling/sd(modeling),
         communication = communication/sd(communication))

df.CIS.scored %>%
  group_by(Lab.type) %>%
  summarize(avg.agency = mean(agency), avg.modeling = mean(modeling), 
            avg.comm = mean(communication), se.agency = sd(agency)/sqrt(n()), 
            se.modeling = sd(modeling)/sqrt(n()), 
            se.comm = sd(communication)/sqrt(n()))

agency.t <- t.test(agency ~ Lab.type, df.CIS.scored %>% 
                     filter(Lab.type != 'Mixed'), conf.level = 0.67)
modeling.t <- t.test(modeling ~ Lab.type, df.CIS.scored %>% 
                       filter(Lab.type != 'Mixed'), conf.level = 0.67)
comm.t <- t.test(communication ~ Lab.type, df.CIS.scored %>% 
                   filter(Lab.type != 'Mixed'), conf.level = 0.67)

fs.diffs <- data.frame(Variable = c('Agency', 'Modeling', 'Communication'),
                       Mean.diff = c(diff(agency.t$estimate),
                                     diff(modeling.t$estimate), 
                                     diff(comm.t$estimate)), 
                       std.error = c(agency.t$stderr, modeling.t$stderr, 
                                     comm.t$stderr))
fs.diffs

theme_set(theme_classic(base_size = 14))
p.agency <- ggplot(df.CIS.scored, aes(x = agency, fill = Lab.type)) +
  geom_density(alpha = 0.6, position = 'identity', adjust = 2) +
  labs(x = 'Agency', y = 'Fraction of labs', fill = 'Lab type') +
  scale_fill_manual(values = c('#e69f00', '#009e74', '#0071b2')) +
  theme(legend.position = 'none') +
  ylim(0, 0.6)

p.modeling <- ggplot(df.CIS.scored, aes(x = modeling, fill = Lab.type)) +
  geom_density(alpha = 0.6, position = 'identity', adjust = 2) +
  labs(x = 'Modeling', y = '', fill = 'Lab type') +
  scale_fill_manual(values = c('#e69f00', '#009e74', '#0071b2')) +
  theme(legend.position = 'top') +
  ylim(0, 0.6) +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

leg.labs <- get_legend(p.modeling)
p.modeling <- p.modeling + theme(legend.position = 'none')

p.communication <- ggplot(df.CIS.scored, aes(x = communication, fill = Lab.type)) +
  geom_density(alpha = 0.6, position = 'identity', adjust = 2) +
  labs(x = 'Communication', y = '', fill = 'Lab type') +
  scale_fill_manual(values = c('#e69f00', '#009e74', '#0071b2')) +
  theme(legend.position = 'none') +
  ylim(0, 0.6) +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

pdf('Figures/Lab_Pedagogy_LabType.pdf', width = 7, height = 3)
grobs = cbind(ggplotGrob(p.agency), ggplotGrob(p.modeling), 
              ggplotGrob(p.communication), size = "first")
grid.arrange(leg.labs, arrangeGrob(grobs), heights = c(1, 10))
dev.off()

cor(df.CIS.scored[, c('agency', 'modeling', 'communication')])
```

### Effect of pedagogical variables on outcomes

#### Setup
```{r}
standardize.vars <- function(df){
  # standardize variables at the class level
  means <- df[!duplicated(df$Class_ID), c('agency', 'modeling', 
                                          'communication')] %>%
  summarize_all(mean)
  sds <- df[!duplicated(df$Class_ID), c('agency', 'modeling', 'communication')] %>%
    summarize_all(sd)
  
  df <- df %>%
    mutate(agency = (agency - means$agency)/sds$agency,
           modeling = (modeling - means$modeling)/sds$modeling,
           communication = (communication - means$communication)/sds$communication)

  return(df)
}

pedagogy.formula <- as.formula('PostScores ~ PreScores + Gender + 
                                Race.ethnicity.AmInd + Race.ethnicity.NatHawaii +
                                Race.ethnicity.Other + Race.ethnicity.Black +
                                Race.ethnicity.Hispanic + Race.ethnicity.Asian + 
                                Race.ethnicity.White + Major + modeling +
                                (1 | anon_institution_id/Class_ID)')

output.stargazer <- function(mod.agency, mod.communication, mod.agency.std, 
                             mod.communication.std, outFile, labels = NULL, 
                             Assessment){
  
  agency.std.coefs <- mod.agency.std$Std_Coefficient
  agency.std.delta <- mod.agency.std$uncertainty
  names(agency.std.coefs) <- names(summary(mod.agency)$coefficients[, 1])
  names(agency.std.delta) <- names(summary(mod.agency)$coefficients[, 2])

  communication.std.coefs <- mod.communication.std$Std_Coefficient
  communication.std.delta <- mod.communication.std$uncertainty
  names(communication.std.coefs) <-
    names(summary(mod.communication)$coefficients[, 1])
  names(communication.std.delta) <- 
    names(summary(mod.communication)$coefficients[, 2])
  
  class(mod.agency) <- "lmerMod"
  class(mod.communication) <- "lmerMod"
  
  out <- stargazer(mod.agency, mod.agency, mod.agency, mod.agency,
                   mod.communication, mod.communication, mod.communication, 
                   mod.communication, 
                 coef = list(summary(mod.agency)$coefficients[, 1],
                             summary(mod.agency)$coefficients[, 2], 
                             agency.std.coefs, agency.std.delta,
                             summary(mod.communication)$coefficients[, 1],
                             summary(mod.communication)$coefficients[, 2], 
                             communication.std.coefs, communication.std.delta),
                 se = list(summary(mod.agency)$coefficients[, 2], NA, 
                           agency.std.delta, NA, 
                           summary(mod.communication)$coefficients[, 2], NA, 
                           communication.std.delta, NA), type = 'latex', 
                 intercept.bottom = TRUE, style = 'asr', 
                 column.labels = c('Beta', 'SE', 'Beta.std', 'SE', 'Beta', 'SE', 
                                   'Beta.std', 'SE'), model.numbers = FALSE,
                 covariate.labels = labels, 
                 dep.var.labels = paste(Assessment, 'posttest scores', sep = ''),
                 out = outFile)
  return(0)
}
```

#### E-CLASS
```{r, include = FALSE}
df.ECLASS.matched.factors <- 
  cbind(df.ECLASS.matched, data.frame(lavPredict(fit.cfa, df.ECLASS.matched,
                                                 method = 'regression'))) %>%
  standardize.vars(.)


mod.ECLASS.agency <- lmer(update(pedagogy.formula, ~. + Race.ethnicity.unknown +
                                   agency), df.ECLASS.matched.factors)
mod.ECLASS.communication <- lmer(update(pedagogy.formula, ~. +
                                          Race.ethnicity.unknown + communication),
                                 df.ECLASS.matched.factors)

mod.ECLASS.agency.std <- standardize_parameters(mod.ECLASS.agency, ci = 0.67)
mod.ECLASS.agency.std$uncertainty <- abs(mod.ECLASS.agency.std$Std_Coefficient - 
                                           mod.ECLASS.agency.std$CI_low)
mod.ECLASS.communication.std <- standardize_parameters(mod.ECLASS.communication, 
                                                       ci = 0.67)
mod.ECLASS.communication.std$uncertainty <- 
  abs(mod.ECLASS.communication.std$Std_Coefficient - 
        mod.ECLASS.communication.std$CI_low)

labels = c("Pretest", "Non-binary", "Unknown", "Woman", "American Indian", 
            "Native Hawaiian", "Other", "Black", "Hispanic", "Asian", "White",
            "LifeSci/Chem", "Engineering", "Math/CS", "Non-science", 
            "Other science", "Undeclared", "Unknown", "Modeling", "Unknown race", 
            "Agency", "Communication", "Constant")

out <- output.stargazer(mod.ECLASS.agency, mod.ECLASS.communication, 
                        mod.ECLASS.agency.std, mod.ECLASS.communication.std, 
                        outFile = 'Pedagogy_ECLASS_Model.tex', labels = labels,
                        Assessment = 'E-CLASS')

print(paste('E-CLASS (agency) marginal R2:', 
            as.numeric(r2(mod.ECLASS.agency)$R2_marginal)))
print(paste('E-CLASS (agency) conditional R2:', 
            as.numeric(r2(mod.ECLASS.agency)$R2_conditional)))

print(paste('E-CLASS (communication) marginal R2:', 
            as.numeric(r2(mod.ECLASS.communication)$R2_marginal)))
print(paste('E-CLASS (communication) conditional R2:', 
            as.numeric(r2(mod.ECLASS.communication)$R2_conditional)))
```

#### PLIC
```{r, include = FALSE}
# some classes with missing CIS info that we remove
df.PLIC.matched <- df.PLIC.matched[complete.cases(df.PLIC.matched),]
summary.datasets(df.PLIC.matched, df.PLIC.matched, df.PLIC.matched)[3,]

df.PLIC.matched.factors <- 
  cbind(df.PLIC.matched, data.frame(lavPredict(fit.cfa, df.PLIC.matched,
                                               method = 'regression'))) %>%
  standardize.vars(.)


mod.PLIC.agency <- lmer(update(pedagogy.formula, ~. + agency),
                        df.PLIC.matched.factors)
mod.PLIC.communication <- lmer(update(pedagogy.formula, ~. + communication),
                               df.PLIC.matched.factors)

mod.PLIC.agency.std <- standardize_parameters(mod.PLIC.agency, ci = 0.67)
mod.PLIC.agency.std$uncertainty <- abs(mod.PLIC.agency.std$Std_Coefficient - 
                                         mod.PLIC.agency.std$CI_low)
mod.PLIC.communication.std <- standardize_parameters(mod.PLIC.communication, 
                                                     ci = 0.67)
mod.PLIC.communication.std$uncertainty <- 
  abs(mod.PLIC.communication.std$Std_Coefficient - 
        mod.PLIC.communication.std$CI_low)

labels = c("Pretest", "Non-binary", "Unknown", "Woman", "American Indian", 
           "Native Hawaiian", "Other", "Black", "Hispanic", "Asian", "White",
           "Engineering", "Other", "Other science", "Unknown", "Modeling",
           "Agency", "Communication", "Constant")

out <- output.stargazer(mod.PLIC.agency, mod.PLIC.communication, 
                        mod.PLIC.agency.std, mod.PLIC.communication.std, 
                        outFile = 'Pedagogy_PLIC_Model.tex', labels = labels, 
                        Assessment = 'PLIC')

print(paste('PLIC (agency) marginal R2:', 
            as.numeric(r2(mod.PLIC.agency)$R2_marginal)))
print(paste('PLIC (agency) conditional R2:', 
            as.numeric(r2(mod.PLIC.agency)$R2_conditional)))

print(paste('PLIC (communication) marginal R2:', 
            as.numeric(r2(mod.PLIC.communication)$R2_marginal)))
print(paste('PLIC (communication) conditional R2:', 
            as.numeric(r2(mod.PLIC.communication)$R2_conditional)))
```

#### Marginal effects plot
```{r}
margEff.plot.pedagogy <- function(mod.agency, mod.communication, 
                                  Assessment, keep.legend = FALSE){
  # average over lab type and gender
  pred.labs.pedagogy <- rbind(data.frame(ggeffect(mod.agency, "agency [-2:2]", 
                                                  ci.lvl = 0.67)) %>%
                                mutate(group = 'agency'), 
                              data.frame(ggeffect(mod.agency, "modeling [-2:2]", 
                                                  ci.lvl = 0.67)) %>%
                                mutate(group = 'modeling'),
                              data.frame(ggeffect(mod.communication, 
                                                  "communication [-2:2]", 
                                                  ci.lvl = 0.67)) %>%
                                mutate(group = 'communication'))
  pred.labs.pedagogy$group <- str_to_title(pred.labs.pedagogy$group)
  pred.labs.pedagogy$group <- factor(pred.labs.pedagogy$group, 
                                     levels = c('Agency', 'Modeling', 
                                                'Communication'))
  
  theme_set(theme_classic(base_size = 16))
  p <- ggplot(pred.labs.pedagogy, aes(x = x, y = predicted, color = group)) +
    geom_line(size = 1) +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), 
                linetype = 2, alpha = 0.1) +
    labs(x = 'Standardized variable', 
         y = paste('Expected ', Assessment, '\nposttest scores', sep = ''), 
         fill = 'Pedagogical variable', color = 'Pedagogical variable') +
  scale_color_manual(values = c('#9F0162', '#00C2F9', '#FF6E3A')) +
  scale_fill_manual(values = c('#9F0162', '#00C2F9', '#FF6E3A')) +
  theme(legend.position = 'top') +
  guides(fill = guide_legend(title.position = 'top', title.hjust = 0.5), 
         color = guide_legend(title.position = 'top', title.hjust = 0.5))

  if(keep.legend){
    leg <- get_legend(p)
    p <- p + theme(legend.position = 'none')
    return(list(p, leg))
  } else {
    p <- p + theme(legend.position = 'none')
    return(p)
  }
}

plot.ECLASS.pedagogy <- margEff.plot.pedagogy(mod.ECLASS.agency, 
                                              mod.ECLASS.communication, 'E-CLASS', 
                                              TRUE)
plot.PLIC.pedagogy <- margEff.plot.pedagogy(mod.PLIC.agency, 
                                            mod.PLIC.communication, 'PLIC', FALSE)
pdf('Figures/Lab_Pedagogy_Effect.pdf', width = 7, height = 4)
grobs = cbind(ggplotGrob(plot.ECLASS.pedagogy[1][[1]]), 
              ggplotGrob(plot.PLIC.pedagogy), size = "first")
grid.arrange(plot.ECLASS.pedagogy[2][[1]], arrangeGrob(grobs), heights = c(2, 10))
dev.off()
```

##### Fraction of marginal effect of lab type
```{r}
expected.fracEffect <- function(std.agency, std.communication, fs.diffs, 
                                lab.effect, lab.effect.se){
  df.agency <- data.frame(std.agency) %>%
    filter(Parameter %in% c('agency', 'modeling'))
  df.communication <- data.frame(std.communication) %>%
    filter(Parameter == 'communication')
  df.effects <- rbind(df.agency, df.communication) %>%
    select(Parameter, Std_Coefficient, uncertainty) %>%
    mutate(Parameter = str_to_title(Parameter))
  df.effects <- df.effects[order(match(df.effects$Parameter, fs.diffs$Variable)),]
  
  df.effects$avg.diff <- df.effects$Std_Coefficient * fs.diffs$Mean.diff
  df.effects$diff.unc <- sqrt((df.effects$uncertainty/
                                 df.effects$Std_Coefficient) ^ 2 +
                                (fs.diffs$std.error/fs.diffs$Mean.diff)^2) * 
    df.effects$avg.diff
  
  df.effects$frac.effect <- df.effects$avg.diff/lab.effect
  df.effects$frac.effect.se <- sqrt((df.effects$diff.unc/
                                       df.effects$avg.diff) ^ 2 + 
                                      (lab.effect.se/lab.effect) ^ 2) * 
    df.effects$frac.effect
  
  return(df.effects)
}

expected.fracEffect(mod.ECLASS.agency.std, mod.ECLASS.communication.std, fs.diffs,
                    diffs.ECLASS[[1]], diffs.ECLASS[[2]])
expected.fracEffect(mod.PLIC.agency.std, mod.PLIC.communication.std, fs.diffs, 
                    diffs.PLIC[[1]], diffs.PLIC[[2]])
```

