---
output:
  html_document: default
  pdf_document: default
---
## Load necessary packages
```{r, message = FALSE, warning = FALSE, echo = FALSE}
library(plyr)
library(readr)
library(tidyverse)
library(DescTools)
library(ggthemes)
library(lmerTest)
theme_set(theme_fivethirtyeight())
```

# Load data and extract classes with both CR and OR

## Old data
```{r}
files = list.files("C:/Users/Cole/Documents/DATA/PLIC_DATA/Raw_Surveys/BC (Before Cole)/", 
                   recursive = TRUE, full.names = TRUE)

files <- files[!grepl('*(UBC119|MAINE)_RAW_POST*', files)]

read.old.file <- function(file){
  df <- read.csv(file)
  df <- df[-1, ]
  df$Survey <- ifelse((df$Q1b != '') | (df$Q4b != ''), 'F', 'C')
  df[df$Q4a == '', 'Q4a'] <- df[df$Q4a == '', 'Q4a.1']
  df <- df %>%
    select(Survey, Q4a)
  
  Name <- strsplit(file, '/')[[1]]
  df$Class_ID <- strsplit(Name[length(Name)], '\\.')[[1]][1]
  return(df)
}

df.old = ldply(files, read.old.file)
```

## New data
```{r}
df.new.post <- read.csv('C:/Users/Cole/Documents/DATA/PLIC_DATA/Collective_Surveys/POST_Valid/POST_Valid_Concat.csv') %>%
  select(Survey, Q4a, Class_ID)
Class_IDs <- unique(df.new.post[df.new.post$Survey == 'F', 'Class_ID'])
df.new.post <- subset(df.new.post, df.new.post$Class_ID %in% Class_IDs) %>%
  mutate(Class_ID = paste(Class_ID, 'post', sep = '.'))

df.new.pre <- read.csv('C:/Users/Cole/Documents/DATA/PLIC_DATA/Collective_Surveys/PRE_Valid/PRE_Valid_Concat.csv') %>%
  select(Survey, Q4a, Class_ID)
Class_IDs <- unique(df.new.pre[df.new.pre$Survey == 'F', 'Class_ID'])
df.new.pre <- subset(df.new.pre, df.new.pre$Class_ID %in% Class_IDs) %>%
  mutate(Class_ID = paste(Class_ID, 'pre', sep = '.'))

df <- rbind(df.old, df.new.post, df.new.pre) %>%
  mutate(Group = as.factor(case_when(
    Q4a == '1' ~ '1',
    Q4a == '2' ~ '2',
    Q4a == '3' ~ 'B',
    TRUE ~ ''
  ))) %>%
  filter(Group != '' & Survey != '') %>%
  select(Survey, Group, Class_ID)
```

# Analysis

## Overall differences

```{r}
df %>%
  group_by(Survey, Group) %>%
  summarize(N = n()) %>%
  mutate(freq = N / sum(N))

chisq.test(df$Survey, df$Group)
```


## Multilevel models

We fit separate Multilevel logit models because pacakges for multinomial models can't handle random effects and packages for mixed effects can't handle multinomial responses. I also ran a chi-squared test to check with accounting for nesting.

```{r}
summary(glmer(Group ~ Survey + (1 | Class_ID), df %>%
                filter(Group != 'B'), family = binomial(link = 'logit')))

summary(glmer(Group ~ Survey + (1 | Class_ID), df %>%
                filter(Group != '2'), family = binomial(link = 'logit')))

summary(glmer(Group ~ Survey + (1 | Class_ID), df %>%
                filter(Group != '1'), family = binomial(link = 'logit')))
```

## What was the frequency in our non-controlled dataset?
```{r}
df.new.pre <- read.csv('C:/Users/Cole/Documents/DATA/PLIC_DATA/Collective_Surveys/PRE_Valid/PRE_Valid_Concat.csv') %>%
  select(Survey, Q4a, Class_ID) %>%
  filter(Survey == 'C' & !is.na(Q4a))

df.new.pre %>%
  group_by(Q4a) %>%
  summarize(N = n()) %>%
  mutate(freq = N / sum(N))

df.new.post <- read.csv('C:/Users/Cole/Documents/DATA/PLIC_DATA/Collective_Surveys/POST_Valid/POST_Valid_Concat.csv') %>%
  select(Survey, Q4a, Class_ID) %>%
  filter(Survey == 'C' & !is.na(Q4a))

df.new.post %>%
  group_by(Q4a) %>%
  summarize(N = n()) %>%
  mutate(freq = N / sum(N))
```

