# Setup

## Load necessary packages
```{r, message = FALSE, warning = FALSE, echo = FALSE}
library(plyr)
library(readr)
library(tidyverse)
library(DescTools)
library(ryouready)
library(reshape2)
library(stringr)
library(ggthemes)
library(cluster)
library(factoextra)
library(DescTools)
theme_set(theme_classic(base_size = 10))
```


## Load data and overview
```{r, echo = FALSE}
info <- data.frame(lapply(read.csv('C:/Users/Cole/Documents/DATA/PLIC_DATA/PLIC_May2019.csv', 
                                   nrows = 1, encoding = 'UTF-8'), 
                          FUN = function(x) gsub("^.*-", "", x)))

full.df <- read.csv('C:/Users/Cole/Documents/DATA/PLIC_DATA/Collective_Surveys/Complete/Complete_Concat_CourseInfo.csv') %>%
  filter(Survey_x == 'C' | Survey_y == 'C') %>% # remove events with no CR surveys
  # remove pre-pandemic data
  mutate(V4_x = as.Date(V4_x),
         V4_y = as.Date(V4_y)) %>%
  filter(V4_y < as.Date('2020-01-01') | (is.na(V4_y) & 
                                           V4_x < as.Date('2020-01-01')))

pre.df <- full.df %>%
  filter(Survey_x == 'C')

experts.df <- read.csv('C:/Users/Cole/Documents/DATA/PLIC_DATA/Experts/OriginalExperts_Scored.csv')

print('Number of pretest survey responses:')
nrow(pre.df)
print('Number of courses in pretest dataset:')
length(unique(pre.df$anon_course_id))
print('Number of classes in pretest dataset:')
length(unique(pre.df$Class_ID))
print('Number of institutions in pretest dataset:')
length(unique(full.df$anon_institution_id))

print('Number of experts:')
nrow(experts.df)
```

I typically use class to refer to the same course in different semesters. So, PHYS 1116 is a course and PHYS 1116 in the fall and spring are two different classes for the same course.

# Analysis

## Question 1e what to do next
```{r, echo = FALSE}
pre.df_1e <- pre.df[, names(pre.df)[(names(pre.df) %like% '^Q1e_\\d*_x$')]]
names(pre.df_1e) <- sub("_x", "", names(pre.df_1e))
cols.1e <- names(pre.df_1e)
pre.df_1e$Respondent <- 'Student'
experts.df_1e <- experts.df[, names(experts.df)[(names(experts.df) %like% 
                                                   '^Q1e_\\d*$')]]
experts.df_1e$Respondent <- 'Expert'

df.1e <- rbind(pre.df_1e, experts.df_1e) %>%
  melt(., measure.vars = cols.1e) %>%
  mutate(value = ifelse(value == 1, 1, 0))

data.frame(t(info[, cols.1e]))

ggplot(df.1e %>%
         filter(value == 1), aes(x = variable, fill = variable)) +
  geom_bar()  +
  ggtitle('Group 1, what to do next') +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 30, hjust = 1)) +
  facet_wrap(~Respondent, scales = 'free_y') +
  geom_text(stat = 'count', aes(label = ..count..), vjust = -0.5, size = 2.5)
```

There's actually pretty good agreement, in general, between students and experts on next steps for Group 1. The lack of masses used really stands out to everybody.

## Question 2e what do do next
```{r, echo = FALSE}
pre.df_2e <- pre.df[, names(pre.df)[(names(pre.df) %like% '^Q2e_\\d*_x$')]]
names(pre.df_2e) <- sub("_x", "", names(pre.df_2e))
cols.2e <- names(pre.df_2e)
pre.df_2e$Respondent <- 'Student'
experts.df_2e <- experts.df[, names(experts.df)[(names(experts.df) %like% 
                                                   '^Q2e_\\d*$')]]
experts.df_2e$Respondent <- 'Expert'

df.2e <- rbind(pre.df_2e, experts.df_2e) %>%
  melt(., measure.vars = cols.2e) %>%
  mutate(value = ifelse(value == 1, 1, 0))

data.frame(t(info[, cols.2e]))

ggplot(df.2e %>%
         filter(value == 1), aes(x = variable, fill = variable)) +
  geom_bar()  +
  ggtitle('Group 2, what to do next') +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 30, hjust = 1)) +
  facet_wrap(~Respondent, scales = 'free_y') +
  geom_text(stat = 'count', aes(label = ..count..), vjust = -0.5, size = 2.5)
```

One of these got cut off (I truncated at any hyphens)...so Q2e_34 is "Compare their k-value to the expected value"

## Question 3, what to do next
```{r, echo = FALSE}
pre.df_3e <- pre.df[, names(pre.df)[(names(pre.df) %like% '^Q3e_\\d*_x$')]]
names(pre.df_3e) <- sub("_x", "", names(pre.df_3e))
cols.3e <- names(pre.df_3e)
pre.df_3e$Respondent <- 'Student'
experts.df_3e <- experts.df[, names(experts.df)[(names(experts.df) %like% 
                                                   '^Q3e_\\d*$')]]
experts.df_3e$Respondent <- 'Expert'
df.3e <- rbind(pre.df_3e, experts.df_3e) %>%
  melt(., measure.vars = cols.3e) %>%
  mutate(value = ifelse(value == 1, 1, 0))

data.frame(t(info[, cols.3e]))

ggplot(df.3e %>%
         filter(value == 1), aes(x = variable, fill = variable)) +
  geom_bar()  +
  ggtitle('Group 2, what to do next, part 2') +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, vjust = 0)) +
  facet_wrap(~Respondent, scales = 'free_y') +
  geom_text(stat = 'count', aes(label = ..count..), vjust = -0.5, size = 2.5)
```

Same thing happened here. Q3e_11 is "Design a new experiment to test the non-zero intercept" and Q3e_36 is "Compare their k-value to the expected value"

I think the big takewaay, similar to the Eco-BLIC is that students favor taking more data (i.e., more trials overwhelmingly), but experts gravitate toward checking assumptions and systematic effects and, to a lesser extent, testing other variables.